---
title: "Proportional Loading"
author: "Jonathan Bourne"
date: "14 February 2018"
output: html_document
editor_options: 
  chunk_output_type: console
---

#THIS WEBSITE IS AMAZING
The most geeky photo graphwebsite ever turns out eccles is a tiny place in the scottish borders
https://www.geograph.org.uk/photo/297432
http://wikimapia.org/19551645/Amersham-Main-Sub-Station

This script is for the PhD chapter/paper on proportional grid loading.

The goal of this paper is to compare real and proportional line limits and see what affect this has on cascading failures in the power-grid during attack.

Open data on powergrid modelling
https://www.sciencedirect.com/science/article/pii/S2352484716300877#f000005


There are 4 lines which are overloaded from the beginning they are given artificial line limits to maintain grid integrity

#Potential journals

Criticital infrastructure protection is the preffered

https://www.journals.elsevier.com/international-journal-of-critical-infrastructure-protection/


https://www.journals.elsevier.com/international-journal-of-electrical-power-and-energy-systems  

https://www.journals.elsevier.com/electric-power-systems-research/


#Setup Block

```{r}

packages <- c("tidyverse", "igraph","readr","readxl", "broom", "zoo", "stringr","xtable", "geomnet", "rlang", "animation", "caret", "modelr", "yardstick", "sf", "rgdal", "RColorBrewer", "geosphere")

new.packages <- packages[!(packages %in% installed.packages()[,"Package"])]
if(length(new.packages)) install.packages(new.packages)


sapply(packages, library, character.only = TRUE)


lapply(packages, library, character.only = TRUE)
library(PowerGridNetworking)

select <- dplyr::select

#Set up file system to read the correct folders this switches between aws and windows mode

basewd <- "/home/jonno/Dropbox/Jonathan_Bourne_Phd_Folder"
datafile <- "/home/jonno/Dropbox/Jonathan_Bourne_Phd_Folder/ETYSAppendixB"
LatexFolder <- "/home/jonno/Dropbox/Apps/ShareLaTeX/Proportional Line Limits" 
FiguresFolder <- file.path(LatexFolder, "Figures")
TablesFolder <- file.path(LatexFolder, "Tables")
MatricesFolder <- file.path(LatexFolder, "Matrices")
Tariff <- file.path(basewd,"Tariff and Transport")
PLwd <- "/media/jonno/Seagate Expansion Drive/ProportionalLoading"
Saved_Sims <- file.path(PLwd, "Saved_Sims")
#Deletion_Order_Folder <-  file.path(PLwd, "DeletionOrder") #Only one of the deletion order folders is needed. Either Nodes or Edges
Deletion_Order_Folder <- file.path(PLwd, "DeletionOrder_Nodes")
StratAttackWd <- "/media/jonno/Seagate Expansion Drive/ProportionalLoading/StratAttack"

#Load necessary datasets and great the base powergrid network
source(file.path("/home/jonno/ProportionalLoading", "CreateGBase.R"))

#Load some other useful functions
list.files("/home/jonno/Useful_PhD__R_Functions", pattern = ".R", full.names = T) %>%
  walk(~source(.x))

#FOr NetSci
#FiguresFolder <- "/home/jonno/Dropbox/Apps/ShareLaTeX/NetSci2018 Poster/Figures"


```

#Create the Attack Orders
```{r}
#Set the path to a large enough storage
setwd(PLwd)

#Ensure there is powerflow
#Remove Dead Ends
g <- RemoveDeadEnds(gbase) 
#saveRDS(gbase, file.path("/home/jonno/Dropbox/AWS_Simulation_Files","gbase.rds"))

#provide correct power flow
g <- g %>%
  PowerFlow(., SlackRef = get.vertex.attribute(., "name")[which.min(get.vertex.attribute(., "Bus.Order"))] )


NetworkStats(g)

mean(betweenness(g, normalized = T))

AttackRounds <- 1000

#Create a reproducible attack order
seed<- 1589
filename <- "DeleteOrders100.rds"
if(file.exists(filename)){
  DeleteOrders <- readRDS(filename)
} else {
set.seed(seed)
DeleteOrders <- MultiAttackOrder(g, Target = "Nodes", 100)  
saveRDS(DeleteOrders, file.path(PLwd, filename))
}

```

#Set alpha colour gradient
```{r}
  AlphaGrad <- scale_colour_gradientn(colors = c("red",   "limegreen"),
                          breaks = c(1,2,7,20,50),
                          trans = "log",
                          values = scales::rescale((c(0, 6, 7, 20, 50))),
                          name = expression(alpha*" level")) #"Alpha value"
```

#Comparison of line limit methods

This section compares artificial line limits created using a variety of metrics

```{r}

alpha_levels <- seq(1, 7, 0.05) #c(1, 1.05, 1.1, 1.2, 1.5, 2, 3, 5, 6,7)
#alpha_levels <- c(1, 1.05, 1.1, 1.2, 1.5, 2, 3, 5,6,7,8,9,10)

EdgeAttr <- get.edge.attribute(g) %>% names %>% 
  map(~{
    data_frame(temp = get.edge.attribute(g, name = .x)) %>%
      set_names(.x)
  }) %>% bind_cols() %>%
   filter(Link.Limit!=1e5, Voltage!=0
         )

EdgeAttr2  <- alpha_levels %>% map(~{

  Proportional_Load(g, .x) %>% 
    get.edge.attribute(., "Link.Limit") %>%
    data_frame(temp = .) %>%
    set_names(paste0("alpha_value_", .x*100))
  
}
) %>% bind_cols() %>%
  filter(get.edge.attribute(g, "Voltage")!=0,
          get.edge.attribute(g, "Link.Limit")!= 1e5)
         
#The results
#This allows us to compare performance of PL edges with the modelled ones.
Limit_Method_RMSE <- EdgeAttr2 %>%
  map_df(~{
   c(postResample(.x, EdgeAttr$Link.Limit) , 
  mean(abs((EdgeAttr$Link.Limit - .x)/EdgeAttr$Link.Limit))) %>%
  matrix %>%
  t %>%
  data.frame() %>% set_names(names(postResample(EdgeAttr$Link.Limit, .x)), "MAPE" )
  
  }) %>%
  mutate(type = names(EdgeAttr2),
         method =  str_split(type, '_(?=[^_]+$)') %>% 
           transpose() %>% 
           .[[1]] %>% 
           unlist,
         Level = str_split(type, '_(?=[^_]+$)') %>% 
           transpose() %>% 
           .[[2]] %>% 
           unlist) %>%
  #This bit converts the Level to numeric. Useful when Only Alpha is being analysed
  mutate(Level = as.numeric(Level)/100)


rm(EdgeAttr); rm(EdgeAttr2)
```

#Alpha dist plot
```{r}
edges <- g %>% as_data_frame %>%
   mutate(alpha = Link.Limit/abs(PowerFlow),
          LoadLevel = 1/alpha,
          PercLL = percent_rank(LoadLevel),
          PercLinkLimit = percent_rank(Link.Limit),
          PercFlow = percent_rank(abs(PowerFlow)))


LabelNames <- round(1/c(-.1, 0, .1,.2,.3,.4,.5,.6,.7,.8,.9,1), 2)
LabelNames[1:2] <- c("", ">10") 

#Uses only Alpha which is much easier for people to understand
 edges %>%
   #filter(alpha>1)%>%
   filter(is.finite(alpha), Link.Limit!= 100000) %>%
   ggplot(aes(x = LoadLevel)) + 
   geom_histogram(bins = 10, aes(y = (..count..)/sum(..count..)))+ #remove the fill to make it black again , fill = rev(AccBarCol[-c(1:2)])
  scale_y_continuous(labels = scales::percent, breaks = seq(0,.5, by= 0.05)) +
   labs(x = expression(alpha*" level"), 
        y ="Percentage of total lines", 
        title = expression("Distribution of "*alpha*" using real line limits under initial conditions")) +
   scale_x_reverse(breaks = seq(1,-.1, by=-0.1), labels= rev(LabelNames))
 ggsave(file.path(FiguresFolder,"LoadLevel.pdf"))

#Calculating the mean alpha level by inverting the load level removes the most wildly massive alpha scores
1/mean(abs(edges$PowerFlow/edges$Link.Limit))

#The median is the same no matter how you calculate it
median(abs(edges$Link.Limit/edges$PowerFlow))


```

#Generate Attack data

##Real line limits

```{r}

setwd(Saved_Sims)

folder <- "Real_Limits"

  if(!file.exists(folder)){
    dir.create(folder)
  }

SaveMultiAttacks(g, DeleteOrders, folder, TotalAttackRounds = AttackRounds, CascadeMode = T)
```


##Topological
Previously called Infinite limits

```{r}

setwd(Saved_Sims)

folder <- "Topological"

  if(!file.exists(folder)){
    dir.create(folder)
  }

SaveMultiAttacks(g, DeleteOrders, folder, TotalAttackRounds = AttackRounds, CascadeMode = F)

```


##PL limits

This function saves networks.
Should the function should be changed so that it can handle edges as well as nodes.

```{r}

#The vector of alpha values to be tested
alpha_vector <- c(1.05, 1.1, 1.2, 1.5, 2, 3, 5, 7, 10, 15, 20, 50)
setwd(Saved_Sims)

#Create the simulations for each of the alpha avalues using 100 simulations for each
alpha_vector %>% walk(~{
  gProp <- Proportional_Load(g, alpha = .x)
  
  folder <- paste0("alpha_value_",  .x*100)
  #create folder if it doesn't already exist
  if(!file.exists(folder)){
    dir.create(folder)
  }
  
  SaveMultiAttacks(gProp, DeleteOrders, folder, TotalAttackRounds = AttackRounds, CascadeMode = T)
  
}
  
)
  
```


##Modelled limits

```{r}
ModelInputVars %>%
  ggplot(aes(x = Link.Limit)) + geom_density()

table(ntile(ModelInputVars$Voltage,3),ntile(ModelInputVars$Link.Limit,3))

table(ntile(ModelInputVars$Voltage,3),ntile(ModelInputVars$Length,3))

table(ntile(ModelInputVars$Link.Limit,4),ntile(ModelInputVars$Elec_Centrality,4))

table(ntile(ModelInputVars$Link.Limit,4), ntile(ModelInputVars$absPF,4), ntile(ModelInputVars$Voltage,3))

table(ntile(ModelInputVars$absPF,4), ntile(ModelInputVars$Voltage,3), ntile(ModelInputVars$Link.Limit,2))

```


```{r}

#Set seed and create model input variables

ModelInputVars <- g %>% as_data_frame %>% left_join(.,  ElectricalCentrality(g)$EdgeEC %>% 
                rename(Elec_Centrality = ElectricalCentrality, Link = Edgename)) %>%
  mutate(absPF = abs(PowerFlow),
         Voltage = as.factor(Voltage),
         Centrality =log10(edge_betweenness(g)+1),
         LengthQuart = ntile(Length, 4),
         absPFQuart = ntile(absPF, 4),
         LogLink.Limit = log10(Link.Limit)) 

#Create set of formula to model line limits
FormulaDF <- formulas(~LogLink.Limit, 
         Voltage_Only = ~ Voltage,
         VoltageLength = ~ Voltage + Length,
         VoltElecCent = ~ Voltage + Elec_Centrality,
         VoltPF = ~ Voltage + absPF,
         PF_Only = ~ absPF ) %>%
  tibble(formulas = .) %>%
  mutate(names = names(formulas)) 

#generate k=10 crossfold validated model
models  <- 1:nrow(FormulaDF) %>% map_df(~{
           print(.x)
           form <- as.formula(FormulaDF %>% pull(formulas) %>% .[[.x]])
    set.seed(1)
    ModelInputVars %>%
      filter(Link.Limit != 1e5) %>%
      crossv_kfold(k = 10) %>%
      #The log limit of the model is used to make it more normally distributed
      mutate(model = map(train, ~lm(form, data = .)
                         ),
              Modelname= FormulaDF %>% pull(names) %>% .[[.x]])#,
          #   ) 

})


#create predictions for each edge in the network
predictions <- models %>%
  unnest(map2(model, test, ~ augment(.x, newdata = .y))) %>%
  mutate(.fitted = 10^.fitted)

ModError<- unique(predictions$Modelname) %>% map_df(~{
  predictions <-  predictions %>% filter(Modelname==.x)
  metrics(predictions , Link.Limit, .fitted) %>% select(-.estimator) %>% spread(key = .metric, value = .estimate) %>%
   bind_cols(tibble(MAPE = mean(abs(predictions$.fitted-predictions$Link.Limit)/predictions$Link.Limit))) %>%
    mutate(Modelname = .x)
  
}) 

ModError %>%
  select(Model = Modelname,  Rsq = rsq, RMSE =rmse, MAPE) %>%
  slice(4:5) %>%
  mutate(Model = c("Volt Power-Flow", "Power-Flow")) %>%
xtable(.,  
       caption = "Accuracy of modelling line-limits", 
       label = "tab:ModError") %>%
   print(type = "latex", file = file.path(FiguresFolder, "ModError.txt"))

#Look at coefficiients
ModStats <- models %>%
  unnest(map(model, ~ tidy(.x))) %>%
   select(.id, term, estimate, Modelname) %>%
   spread(key = term, value = estimate) %>% 
   select(-.id) 
   
# bind_rows(ModStats %>% group_by(Modelname) %>% summarise_all(mean) %>% mutate(type = "mean"),
#               ModStats%>% group_by(Modelname) %>% summarise_all(sd) %>% mutate(type = "sd")) %>%
#      select(type, everything()) %>%
#    #  mutate_if(is.numeric, signif, digits = 2) %>%
# xtable(.,  
#        caption = "Mean model coefficients and standard deviation across 10-fold cross-validation", 
#        label = "tab:ModCoeffs") %>%
#    print(type = "latex", file = file.path(FiguresFolder, "ModCoeffs.txt"))
 
#Just print the two models. remove re
ModStats %>% group_by(Modelname) %>% summarise_all(mean) %>%
  slice(c(1,5)) %>%
  select(-Elec_Centrality,-Length) %>%
  mutate(absPF = absPF*1e4,
         Modelname = case_when(
           Modelname == "PF_Only" ~ "PF Model",
           TRUE ~ "PF & Voltage Model"
         )) %>%
  gather(key = Coefficients, value = value2, -Modelname) %>%
  spread(key = Modelname, value = value2) %>%
  mutate(Coefficients = case_when(
    Coefficients == "absPF" ~"PF (in 1000s)",
    Coefficients == "(Intercept)" ~ "Intercept",
    Coefficients == "Voltage275" ~"Voltage 275",
    TRUE ~"Voltage 400"
  )) %>%
xtable(.,  
       caption = "Mean model coefficients from 10-fold cross-validation", 
       label = "tab:ModCoeffs") %>%
   print(type = "latex", file = file.path(FiguresFolder, "ModCoeffs.txt"))

#Create simulations for all the models
rev(unique(predictions$Modelname)) %>% walk(~{ #makes the sims used in the paper first
#Create new edge limits using the predictions 
NewEdges <- tibble(Link = get.edge.attribute(g, "Link") ) %>%
  left_join(., predictions %>% filter(Modelname ==.x)) %>%
  mutate(.fitted = ifelse(is.na(.fitted), 1e5, .fitted))

LinModLims <- set_edge_attr(g, "Link.Limit", value = NewEdges$.fitted)
#saveRDS(LinModLims, file.path(PLwd, "LinModLims.rds"))
#Generate simulations
setwd(Saved_Sims)

folder <- paste0("Model_",.x )

  if(!file.exists(folder)){
    dir.create(folder)
  }

SaveMultiAttacks(LinModLims, DeleteOrders, folder, TotalAttackRounds = AttackRounds, CascadeMode = T)

}
)

test <-tibble(PF = predictions %>% filter(Modelname =="PF_Only") %>% pull(.fitted),
       VoltPF = predictions %>% filter(Modelname =="VoltPF") %>% pull(.fitted),
       )

cor(test$PF, test$VoltPF)

test %>%
  ggplot(aes(x = PF, y = VoltPF)) + geom_point() + scale_x_log10() + scale_y_log10()

```

#Extracting stats

Extracting stats is slow this extracts the stats and saves them as a file.

```{r}

ExtractAttackStats(Saved_Sims, file.path(PLwd, "SummaryData"))

#Load the saved files
AttackRoundData <- list.files(path = file.path(PLwd,"SummaryData"), 
                              pattern = ".rds", 
                              full.names = TRUE) %>%
   map_df(~read_rds(.x)) %>%
  mutate(GCfract = ifelse(is.finite(GCfract), GCfract, 1)) #GCfract turns to infinity at the end this needs to be corrected



```

#Expand data
This chunk keeps the times series for as long as at least 1 alpha is collapsing.
```{r}

ExpandedDF <- 1:100 %>% map_df(~{
    SimAttack <- AttackRoundData %>%
      filter(simulationID == .x) %>%
      select(alpha, NodesAttacked) %>% 
      mutate(value = 1) %>%
      spread(key = alpha, value) %>%
      gather(key = alpha, value = value, -NodesAttacked) %>%
      mutate(simulationID = .x) %>%
      select(-value)
})


AttackRoundDataExpanded <- ExpandedDF  %>%
  left_join(., AttackRoundData%>%
  select(-GCfract, -Blackout), by = c("NodesAttacked", "simulationID", "alpha")) %>%
  mutate_if(is.numeric, .funs = ~{ifelse(is.finite(.x), .x, 0)})


AttackRoundDataExpanded2 <- ExpandedDF  %>%
  left_join(., AttackRoundData%>%
  select(NodesAttacked, simulationID, alpha ,GCfract, Blackout), by = c("NodesAttacked", "simulationID", "alpha")) %>%
  mutate_if(is.numeric, .funs = ~{ifelse(is.finite(.x), .x, 1)})

AttackRoundDataExpanded <-left_join(AttackRoundDataExpanded, AttackRoundDataExpanded2)
    
AttackRoundData <- AttackRoundDataExpanded

rm(AttackRoundDataExpanded);rm(AttackRoundDataExpanded2); rm(ExpandedDF)
```


#Construct attack summaries

Plots simple graphs from summary data

```{r}

SummaryofGC <- AttackRoundData %>%
  mutate(GridLoading = case_when(
    Blackout==1 ~0,
     TotalEdges == 0 ~0,
     TRUE ~GridLoading
  )
         )  %>% #After redoing all the extract stats remove this line
  SummariseMultiAttack(., groupingvar = alpha) %>%
  mutate(PercNum = NodesAttacked/vcount(g),
         alpha = sub("alpha_value_", "", alpha) %>% sub("_", " ", .))


PNodeDens <-  AttackRoundData %>%
  mutate(PercNum = round(NodesAttacked*100/vcount(g)),
            LoadDrop = (first(GridLoading)-GridLoading)/first(GridLoading))


 NodeCollapse <- rbind(SummaryofGC %>%
  select(PercNum, mean, alpha, GC05, GC95, sd) %>% 
    mutate(type = "Giant componant size reduction"),
SummaryofGC %>% 
  select(PercNum, mPGfract, alpha, PG05, PG95, sdPGfract) %>% 
  mutate(type = "Blackout size") %>%
  rename(mean = mPGfract, GC05 = PG05, GC95 = PG95, sd = sdPGfract)
) %>% mutate(Target = "Node") %>%
   filter(alpha != "Constant 105", alpha != "Constant Volt_105" )

 NodeCollapse2<- NodeCollapse %>%
   filter(!is.na(as.numeric(alpha))) %>%
   mutate(alpha = as.numeric(alpha)/100) %>%
   arrange(alpha)
 
AlphaCollapse <- NodeCollapse2 %>%
       filter(is.finite(sd))#need to remove infinte values 

RealCollapse <- NodeCollapse %>% 
               filter(alpha == "Real Limits",is.finite(sd))#need to remove infinte values 
   
ModelledCollapse <- NodeCollapse %>% 
               filter(alpha == "Model PF_Only",is.finite(sd))#need to remove infinte values 

ModelledCollapse2 <- NodeCollapse %>% 
               filter(alpha == "Model VoltPF",is.finite(sd))#need to remove infinte values 

TopoCollapse <- NodeCollapse %>% 
               filter(alpha == "Topological",is.finite(sd))#need to remove infinte values 



NameOrder <- tibble(name = c("Real", "PF","Volt PF", "Topological"), 
                    Colour = c("black", "blue", "magenta3", "grey50")) %>% 
  arrange(name)

AlphaCollapse %>% #need to remove infinte values 
  ggplot(aes(x = PercNum, y =  mean, group = alpha)) + 
  geom_line(aes(colour = as.numeric(alpha)), show.legend = TRUE) +  
  AlphaGrad +
  geom_line(data = RealCollapse, aes(fill = 'Real'), color = 'black', linetype ="longdash") +
  geom_line(data = ModelledCollapse, aes(fill = 'PF Model'), color = 'blue', linetype ="longdash") +
  geom_line(data = ModelledCollapse2, aes(fill = 'Volt PF'), color = "magenta3", linetype ="longdash") +
  geom_line(data = TopoCollapse, aes(fill = 'Topological'), color = 'grey50', linetype ="longdash") +
  scale_fill_manual("Line Limit", values=c(1, 1, 1, 1),
                    labels = NameOrder$name,
        guide=guide_legend(override.aes = list( colour=NameOrder$Colour))) +
  facet_grid(~type) +
  scale_x_continuous(labels=scales::percent) + 
  scale_y_continuous(labels=scales::percent) +
  coord_cartesian(x = c(0,0.5)) +
  labs(title = "Change in Giant componant and Blackout size as nodes are attacked" , 
       x = "Percent of elements attacked", 
       y = "Performance drop")
 
 ggsave(file.path(FiguresFolder,"GCandBlackoutChange.pdf"))


 AlphaCollapse %>% #need to remove infinte values 
  ggplot(aes(x = PercNum, y =  sd, group = alpha)) + 
  geom_line(aes(colour = as.numeric(alpha)), show.legend = TRUE) +  
  AlphaGrad +
  geom_line(data = RealCollapse, aes(fill = 'Real'), color = 'black', linetype ="longdash") +
  geom_line(data = ModelledCollapse, aes(fill = 'PF Model'), color = 'blue', linetype ="longdash") +
  geom_line(data = ModelledCollapse2, aes(fill = 'Volt PF'), color = "magenta3", linetype ="longdash") +
  geom_line(data = TopoCollapse, aes(fill = 'Topological'), color = 'grey50', linetype ="longdash") +
  scale_fill_manual("Line Limit", values=c(1, 1, 1, 1),
                    labels = NameOrder$name,
        guide=guide_legend(override.aes = list( colour=NameOrder$Colour))) +
  facet_grid(~type) +
  scale_x_continuous(labels=scales::percent) + 
  scale_y_continuous(labels=scales::percent) +
  coord_cartesian(x = c(0,0.5)) +
  labs(title = "Standard deviation of damage across all simulations" , x = "Percent of elements attacked", y = "Standard deviation of damage")
 ggsave(file.path(FiguresFolder,"SDchange.pdf"))

 
```


#Modelled only
```{r}
 
NodeCollapse %>%
   filter(is.finite(sd)) %>%
 # filter(grepl("PF", alpha)|alpha == "Real Limits") %>%
   filter(is.na(as.numeric(alpha)))%>% #need to remove infinte values 
  ggplot(aes(x = PercNum, y =  mean, group = alpha)) + 
  geom_line(aes(colour = alpha), show.legend = TRUE) +  
  facet_grid(~type) +
  #scale_color_brewer(type = "div", palette = "Dark2")+
  scale_x_continuous(labels=scales::percent) + 
  scale_y_continuous(labels=scales::percent) +
  coord_cartesian(x = c(0,0.5))+
  labs(title = "Standard deviation of damage across all simulations" , x = "Percent of elements attacked", y = "Standard deviation of damage")


 NodeCollapse %>%
   filter(is.finite(sd)) %>%
   filter(is.na(as.numeric(alpha)))%>% #need to remove infinte values 
#  filter(grepl("PF", alpha)|alpha == "Real Limits") %>%
  ggplot(aes(x = PercNum, y =  sd, group = alpha)) + 
  geom_line(aes(colour = alpha), show.legend = TRUE) +  
  facet_grid(~type) +
  scale_x_continuous(labels=scales::percent) + 
  scale_y_continuous(labels=scales::percent) +
  coord_cartesian(x = c(0,0.5))+
  labs(title = "Standard deviation of damage across all simulations" , x = "Percent of elements attacked", y = "Standard deviation of damage")
 
```


#FInding alpha

This chunk shows that you can infer the mean value of the network by looking at the loading change under attack.
Probably only about 10% of the network needs to be attacked
```{r}
RealAlpha <- AttackRoundData %>%
   group_by(alpha, NodesAttacked) %>%
   summarise(Mean = mean(GridLoading),
             counts = n()) %>%
  ungroup %>%
  mutate(PercNum = NodesAttacked/vcount(g),
         type = "Load level")   %>% 
  filter(PercNum<0.25) 

RealAlpha <- RealAlpha %>%
  bind_rows(., RealAlpha %>% mutate(Mean = 1/Mean, type = "alpha"))

RealAlpha %>%
  filter(grepl("alpha", alpha)) %>%
   CleanNames(., "alpha", AlphaOrder) %>%
  mutate(alphaNum = gsub("alpha value ", "", alpha2) %>% as.numeric(.)) %>%
  ggplot(aes(x = PercNum, y  = Mean, colour = alphaNum, group = alpha)) +
    geom_line() + 
  AlphaGrad +
   geom_line(data = RealAlpha %>%
               filter(grepl("Model_VoltPF", alpha)), 
             aes(fill = 'Real'), color = 'black', linetype ="longdash")  +
  scale_x_continuous(labels=scales::percent) + 
  coord_cartesian(x = c(0,0.2))+
  labs(title =  expression("Mean "*alpha*" value and mean Load level during attack")  , 
       x = "Percent of elements attacked", 
       y = "Mean grid level") +
  facet_wrap(~type, scales = "free_y")
 ggsave(file.path(FiguresFolder,"AlphaChange.pdf"))


 
#Model loadings have much small errors and do not follow the same rule as proportional loading
RealAlpha %>%
  filter(!grepl("alpha", alpha)) %>%
   CleanNames(., "alpha", AlphaOrder) %>%
  ggplot(aes(x = PercNum, y  = Mean, colour = alpha2, group = alpha2)) +
    geom_line() +
  facet_wrap(~type, scales = "free_y")

normalize <- function(x){
  return((x-min(x)) / (max(x)-min(x)))
}

RealAlpha %>%
  filter(is.finite(Mean)) %>% #there are couple of Nans at the end of the run. I don't know why. It doesn't seem important and so I have deleted.
  group_by(alpha, type) %>%
  summarise(diff = abs(max(Mean)-min(Mean))) %>%
  group_by(type) %>%
  mutate(normval = normalize(diff)) %>%
  group_by(alpha) %>%
  summarise(totdiff = sum(normval)) %>%
   CleanNames(., "alpha", AlphaOrder) %>%
  filter(grepl("alpha", alpha)) %>%
    mutate(alphaNum = gsub("alpha value ", "", alpha2) %>% as.numeric(.)) %>%
  filter(alphaNum!=50) %>%
  ggplot(aes(x = alphaNum, y = totdiff))+ geom_line() +
    theme(legend.position = "none", 
        axis.text.x = element_text(angle = 45, hjust = 1)) +
  labs(x = "Alpha", y = "Sum of max absolute change in alpha and Load", 
       title = expression("Finding the true load level of a network by measuring the change \nin load level and alpha over and attack"))
 ggsave(file.path(FiguresFolder,"FindTrueAlpha.pdf"))  

```


#Deletion similarity

##Round Deleted

Get the round number that an edge was deleted.

```{r}

FolderVect <- list.files(path = Saved_Sims) #folder where all the alpha FOLDERS are
FileVect <- list.files(path = Deletion_Order_Folder) %>% gsub(".rds", "",.) #folder where all the deletion order FILES are
new.type <- FolderVect[!(FolderVect %in% FileVect)] #The FOLDERS that are not present as FILES



  if(!file.exists(Deletion_Order_Folder)){
    dir.create(Deletion_Order_Folder)
  }


if(length(new.type)>0){
file.path(Saved_Sims, new.type) %>%
  walk( ~{
    print(.x) #print name of folder where deletion order will be calculated
    
  Removeddf <- list.files(path = .x, full.names = TRUE) %>% #list the different network of network rds files present
    map_df(~{
        file <- .x
        print(file)
        read_rds(file) %>%
          RoundTypeRemoved (.)  %>%
          mutate(Sim = gsub(".rds", "",file) %>% basename)
      }
    ) %>%
    group_by(Sim) %>%
    mutate(RoundRemoved = ifelse(is.na(RoundRemoved), max(RoundRemoved), RoundRemoved),
         alpha = basename(.x)) %>% 
    ungroup

  Removeddf %>%
        write_rds(x = ., paste0(file.path(Deletion_Order_Folder,basename(.x)), ".rds"))
  }
  )

} 
  
AllRemovedNodes <- list.files(Deletion_Order_Folder, full.names = TRUE) %>%
  map_df(~read_rds(.x))

```

##Number of round per line-type

This chunk plots the number of rounds til complete collapse 
The islanding and overloading
```{r}

AlphaOrder <- c("alpha value 1","alpha value 1.05","alpha value 1.1","alpha value 1.2","alpha value 1.5","alpha value 2" ,"alpha value 3","alpha value 5","alpha value 6","alpha value 7","alpha value 10","alpha value 15","alpha value 20","alpha value 50","Topological" ,"PF Model", "Volt PF Model")  

#Check number of rounds
 NumberofRounds <- AllRemovedNodes %>%
  group_by(Sim, alpha, type) %>%
  summarise(counts = max(RoundRemoved, na.rm = T)) %>%
   ungroup %>% mutate( RemovalType = "Rounds") %>%
   filter(grepl("(alpha)|(Topological)|(PF_Only)", alpha))

 
 #Plot the number of rounds this is not a very useful thing to know
NumberofRounds %>%
  filter(type== "Node") %>%
  CleanNames(., "alpha", AlphaOrder) %>%
  mutate( alpha = ifelse(alpha== "Topological","Inf", alpha),
         alpha = gsub("alpha_value_", "", alpha),
         alpha = as.numeric(alpha)/100
) %>%
  ggplot(aes(x = alpha2, y = counts)) + geom_boxplot()+
    theme(legend.position = "none", 
        axis.text.x = element_text(angle = 45, hjust = 1)) 


test <- AllRemovedNodes %>%
  group_by(type, alpha, Sim, RemovalType) %>%
  summarise(counts = n()) %>%
  spread(key = RemovalType, value = counts) %>%
  ungroup
  
test %>%
  filter(alpha !="Topological") %>%
  select(Islanded:Targeted) %>%
  cor

 AllRemovedNodes %>%
    CleanNames(., "alpha", AlphaOrder) %>%
   filter(!grepl("alpha", alpha)) %>% #don't plot alpha values
  group_by(type, alpha2, Sim, RemovalType) %>%
  summarise(counts = n()) %>%
 #bind_rows(., NumberofRounds) %>%
     filter(type == "Node") %>%
   ggplot(aes(x = alpha2, y = counts)) + geom_boxplot() + 
   facet_wrap(RemovalType~type, scales = "free_y")+
    theme(legend.position = "none", 
        axis.text.x = element_text(angle = 45, hjust = 1)) 

 
  AllRemovedNodes %>%
      CleanNames(., "alpha", AlphaOrder) %>%
  group_by(type, alpha2, Sim, RemovalType) %>%
  summarise(counts = n()) %>%
    filter(type == "Node", RemovalType !="Islanded") %>%
     spread(key = RemovalType, value = counts) %>%
    rename(Rounds = Targeted) %>%
ggplot(aes(x = Overloaded, y = Rounds, colour = alpha2))  + geom_point() +
    ggtitle("Number of Rounds vs number of overloaded nodes")
 
  
test <-  AllOutcomes %>%
    mutate(ProbClass = cut(Probs, (0:9)/10, include.lowest = T, labels = (1:9)/10)) %>%
    group_by(ProbClass, Class) %>%
    summarise(counts = n()) %>%
  ungroup %>%
  mutate(ProbClass = as.character(ProbClass) %>% as.numeric(.)) %>%
    arrange(-ProbClass) %>%
    group_by(Class) %>%
    mutate(Cumsum = cumsum(counts),
           CumPerc = Cumsum/length(unique(AllOutcomes$pd_profileID))) %>%
  ungroup

test %>%
    ggplot(aes(x = ProbClass, y = CumPerc, colour = Class, group = Class)) + geom_line()+
  labs(x= "The probability of being class", y = "The Percent of total data that is this class")
  
```

##Islanding per round

This chunk shows that islanding takes place at a constant rate
```{r}
 LossFractionByRound <- AllRemovedNodes %>%
  group_by(Sim, alpha, type, RoundRemoved, RemovalType) %>%
  summarise(counts = n()) %>%
  group_by(Sim, alpha, type, RemovalType) %>%
  mutate(cumsum = cumsum(counts)) %>%
  group_by(alpha, type, RoundRemoved, RemovalType) %>%
  summarise(mean = mean(counts),
            median = median(counts),
            sd = sd(counts),
            cummean = mean(cumsum),
            cummedian = median(cumsum),
            cumsd = sd(cumsum)) %>%
  left_join(tibble(type = c("Edge", "Node"), 
                    tot = c(ecount(gbase), vcount(gbase)))
            ) %>%
  group_by(alpha, type, RemovalType) %>%
  mutate( test = cumsum(median),
          testfrac = test/tot,
    cummeanfrac = cummean/tot,
            cummedianfrac = cummedian/tot)

LossFractionByRound %>%
  filter(type == "Node", RemovalType != "Targeted") %>%
  ggplot(aes(x = RoundRemoved, y = cummean, group = alpha, colour = alpha)) + geom_line() + 
  facet_wrap(~RemovalType)
  
Loss2 <- AllRemovedNodes %>%
  group_by(Sim, alpha, type, RoundRemoved, RemovalType) %>%
  summarise(counts = n()) %>%
  group_by(Sim, alpha, type, RemovalType) %>%
  mutate(cumsum = cumsum(counts)) 

Loss2 %>%
  filter(type == "Node", alpha == "alpha_value_300", RemovalType != "Targeted") %>%
  ggplot(aes(x = RoundRemoved, y = cumsum, group = Sim, colour = alpha)) + geom_line() + 
  facet_wrap(.~RemovalType, scales = "free_y")

Loss3 <- Loss2 %>%
  group_by(Sim, type, alpha, RemovalType) %>%
  summarise(cumsum = max(cumsum)) %>%
  spread(key = RemovalType, value = cumsum)

#Strong negative corellation with between Targeted and overload for edge removal, but also for Islanded... What?
Loss3 %>%
  filter(type == "Node", alpha == "Real_Limits") %>%
  ggplot(aes(x = Islanded, y = Overloaded)) +
  geom_point()

   Loss3 %>%
 # filter(type == "Node", alpha == "Real_Limits") %>%
     group_by(alpha, type) %>%
     summarise(corTargOver = cor(Targeted, Overloaded, use =  "pairwise.complete.obs"),
               corTargIsl = cor(Targeted, Islanded, use =  "pairwise.complete.obs"),
               corOverIsl = cor(Overloaded, Islanded, use =  "pairwise.complete.obs")) %>%
     arrange(type)
  
```


##Plot Correlation

This needs to be edited to account for the changed in the RoundRemoved function that differentiate between Overload/Targeted or Unknown removal types. 

```{r}
# testList <- file.path("/media/jonno/Seagate Expansion Drive/ProportionalLoading/Saved_Sims/Linear_Model_Limits",
#                   "Simulation_ID_1.rds") %>% 
#   read_rds

AllRemovedEdges <- AllRemovedNodes %>%
  filter(type == "Node")

#Get only the real limits
RealPreCor  <- AllRemovedEdges %>%
  filter(alpha == "Real_Limits") %>%
  select(-alpha)

#Add the real limits onto the other nodes to allow direct comparison
#Filter out the NA values
PreCorRemoved  <- AllRemovedEdges %>%
  filter(alpha != "Real_Limits") %>%
  left_join(., RealPreCor, by = c("Name", "Sim")) %>%
  mutate(RoundRemoved.x = ifelse(RemovalType.x=="Targeted", NA, RoundRemoved.x ),
         RoundRemoved.y = ifelse(RemovalType.x=="Targeted", NA, RoundRemoved.y ))


AllCombos <- PreCorRemoved  %>% distinct(alpha, Sim)

#Cycle through all the combinations of alpha and sim to get the corellation for all
#If the relationship is co-incidental then when this is scrambled the results should be junk 
 PreAlphavsCor <- map2_df(.x = AllCombos$Sim, .y = AllCombos$alpha, ~{
   
    temp <- PreCorRemoved %>%
    filter(Sim == .x, alpha == .y, 
           complete.cases(.) #removes NA values
           ) #%>% #converting to rank does nothing as I guess tie breaks are already in place
     # mutate(RoundRemoved.x = rank(RoundRemoved.x),
    #         RoundRemoved.y = rank(RoundRemoved.y))
      cor(temp$RoundRemoved.x, temp$RoundRemoved.y, method = "spearman") %>%
        tibble(Sim = .x, alpha = .y, cor =.)
    
  })


#"Infinite Limits"
AlphaOrder <- c("alpha value 1.05","alpha value 1.1","alpha value 1.2","alpha value 1.5","alpha value 2" ,"alpha value 3","alpha value 5","alpha value 7","alpha value 10","alpha value 15",
                "alpha value 20","alpha value 50","Topological" ,"PF Model", "Volt PF Model",
                "Model Volt PF")  

#Pre process data for plot
 AlphavsCor <-  PreAlphavsCor %>% 
     mutate(alpha = case_when(
       alpha == "Model_PF_Only"~ "PF_Model",
       alpha == "Model_VoltPF" ~ "Volt_PF_Model",
       TRUE ~ alpha)
           ) %>%
   filter(grepl("PF_Model", alpha)| grepl("Topological", alpha)|grepl("alpha", alpha)|grepl("Volt_PF_Model", alpha)) %>%  
   CleanNames(., "alpha", AlphaOrder) %>%
  mutate( alpha = ifelse(alpha== "Topological","Inf", alpha),
         alpha = gsub("alpha_value_", "", alpha),
         alpha = as.numeric(alpha)/100
)
 
 #Make temporary plot
 #This is used so that the blue can be added on for the linear line limits
 TempPlot <- AlphavsCor %>%
  ggplot(aes(x = alpha2, y = cor, fill = alpha)) + geom_boxplot()+
  scale_fill_gradientn(colors = c("red",   "limegreen"),
                          breaks = c(1,2,7,20,50),
                          trans = "log",
                          values = scales::rescale((c(0, 6, 7, 20, 50))))

#Extract the colour codes from the ggplot object.
AccBuild <- ggplot_build(TempPlot)
AccBarCol <- c(unique(AccBuild$data[[1]][[1]]), "blue", "magenta3")
names(AccBarCol) <-AlphavsCor$alpha2 %>%  levels
rm(TempPlot)

AlphavsCor %>%
    ggplot(aes(x= alpha2, y = cor, fill = alpha2)) +
  geom_boxplot() +
   scale_fill_manual(values= AccBarCol) +
  scale_y_continuous( breaks = seq(0,1, by= 0.1)) +
  theme(legend.position = "none", 
        axis.text.x = element_text(angle = 45, hjust = 1)) +
  labs(x = expression(alpha*" level"), y ="Correlation with real line limits", title= "Node removal rank correlation against real limits")

ggsave(file.path(FiguresFolder, "CorBoxPlot.pdf"))

AlphavsCor %>% 
  group_by(alpha2) %>%
  summarise(mean= mean(cor, na.rm = T),
            median = median(cor, na.rm = T),
            sd = sd(cor, na.rm = T)) %>%
  arrange(-mean)


#Check the number of NA values
#Na values arethe nodes that were targeted for removal. They are therefore removed from the simulation
HowManyNAs <- PreCorRemoved %>%
  group_by(alpha, Sim) %>%
  summarise(counts = sum(is.na(RoundRemoved.x*RoundRemoved.y)))

HowManyNAs %>%
  ggplot(aes(x = as.factor(alpha), y = counts)) + geom_boxplot()


test <-tibble(x = 1:10, y = 1:10)

1:10 %>% map_dbl(~{
set.seed(.x)
test2 <-test %>% sample_n(.,nrow(.))
print(test2)
cor(test2$x, test2$y, method = "spearman")
})




test <- tibble(NodeID = LETTERS[1:5], Base = c(1,2,3,4,5), Other.1 = c(1,2,3,5,4), Other.2 = c(1,5,3,4,2))

dist(t(test[,-1]))

cor((test[,-1]), method = "spearman")

```

The order in which the nodes are targeted is random
I compare the round in which a node is removed from the network between real line limits and alpha = x. Using your vectors this gives the following.
table A
  NodeID  Base Other.1 Other.2
1 A          1       1       1
2 B          2       2       5
3 C          3       3       3
4 D          4       5       4
5 E          5       4       2

The corellation matrix for this is
table C
        Base Other.1 Other.2
Base     1.0     0.9     0.1
Other.1  0.9     1.0     0.3
Other.2  0.1     0.3     1.0

which generally agrees with the euclidean distance, which gives them a similar relationship in terms of similarity rankings
table C
            Base  Other.1
Other.1 1.414214         
Other.2 4.242641 3.741657

Re-ordering the rows of table A does not affect the euclidean distance or the corellations. 
As the targeting order between simulations is random, then if the order had co-incidently created a pattern, this would not happen in the majority of the other attacks.


#Damage analysis
This can be expanded to look at different metrics
```{r}

BasePlot <- function(df){
#Sets up the plot for comparing different metrics, the metric of choice info is then added on
  df %>%
    ggplot(aes(x= alpha2, fill = alpha2)) +
    theme(legend.position = "none",  
        axis.text.x = element_text(angle = 45, hjust = 1))+
   scale_fill_manual(values= AccBarCol) + #requires the colours that have been previously calculated in the boxplot chunk
  scale_y_continuous( breaks = seq(0,1, by= 0.1))
  
  }

AccuracyAnalysis <- AttackRoundData %>%
     filter(grepl("(alpha)|(Topological)|(PF_Only)|(Real_Limits)|(Model_VoltPF)", alpha)) %>%
       mutate(alpha = case_when(
       alpha == "Model_PF_Only"~ "PF_Model",
       alpha == "Model_VoltPF" ~ "Volt_PF_Model",
       TRUE ~ alpha)
       ) 

AccuracyAnalysis %>%
  DamageComparison(., "Blackout", AlphaOrder) %>%
  select(-SimulationID,-alpha) %>%
  group_by(alpha2) %>%
  summarise_all(funs(mean, median)) %>%
  arrange(RMSE_mean)

AccuracyAnalysis %>%
#  filter(is.finite(GCfract)) %>%
  DamageComparison(., "GCfract", AlphaOrder) %>%
  select(-SimulationID,-alpha) %>%
  group_by(alpha2) %>%
  summarise_all(funs(mean, median)) %>%
  arrange(RMSE_mean)

SDAnalysis <- AccuracyAnalysis %>%
  group_by(NodesAttacked, alpha) %>%
  summarise(GCfract = sd(GCfract),
            Blackout = sd(Blackout)) %>%
  mutate(simulationID = 1)

SDAnalysis %>%
  DamageComparison(., "Blackout", AlphaOrder) %>%
  select(-SimulationID,-alpha) %>%
  group_by(alpha2) %>%
  summarise_all(funs(mean, median)) %>%
  arrange(RMSE_mean)

SDAnalysis %>%
  DamageComparison(., "GCfract", AlphaOrder) %>%
  select(-SimulationID,-alpha) %>%
  group_by(alpha2) %>%
  summarise_all(funs(mean, median)) %>%
  arrange(RMSE_mean)


AccPlot <- AccuracyAnalysis %>%
  DamageComparison(., "Blackout", AlphaOrder) %>% BasePlot

 AccPlot + geom_boxplot(aes(y = RMSE)) +
  labs(x = expression(alpha*" level"), 
       title = expression("Blackout RMSE against real line limits for all calculated "*alpha*" levels") )
ggsave(file.path(FiguresFolder, "RMSEChange.pdf"))



AttackRoundData %>% as_tibble %>%
     filter(!grepl("alpha", alpha)) %>%
       mutate(alpha = ifelse(alpha == "Model_PF_Only", "PF_Model", alpha)) %>%
  DamageComparison(., "Blackout", AlphaOrder) %>%
  group_by(alpha) %>%
  summarise_if(is.numeric, mean)

#Why are there NA's?
AttackRoundData %>%
     filter(!grepl("alpha", alpha)) %>%
       mutate(alpha = ifelse(alpha == "Model_PF_Only", "PF_Model", alpha)) %>%
  DamageComparison(., "GCfract", AlphaOrder) %>%
  group_by(alpha) %>%
  summarise_if(is.numeric, mean)

```


#Strategy difference

See the difference between strategies
##Different strategies 1 load level
```{r}
#The vector of alpha values to be tested
StratAttackVect <- CreateStrategyAttackDf(g)

alpha_vector <- c(1.05, 1.1,1.5, 2, 5,  10, 20, 50)

setwd(StratAttackWd)

#Create the simulations for each of the alpha avalues using 100 simulations for each
alpha_vector %>% walk(~{
    gProp <- Proportional_Load(g, alpha = .x)
    
    folder <- paste0("alpha_value_",  .x*100)
    #create folder if it doesn't already exist
    if(!file.exists(folder)){
      dir.create(folder)
    }
    
    SaveMultiAttacks(gProp, StratAttackVect, folder, TotalAttackRounds = AttackRounds, CascadeMode = T)
    
  }
  
)

setwd(StratAttackWd)
folder <- "Real_Limits"

  if(!file.exists(folder)){
    dir.create(folder)
  }

SaveMultiAttacks(g,  StratAttackVect, folder, TotalAttackRounds = AttackRounds, CascadeMode = T)

setwd(StratAttackWd)
folder <- "Topological"

  if(!file.exists(folder)){
    dir.create(folder)
  }

SaveMultiAttacks(g, StratAttackVect, folder, TotalAttackRounds = AttackRounds, CascadeMode = F)

setwd(StratAttackWd)
folder <- "Model_PF_Only"

  if(!file.exists(folder)){
    dir.create(folder)
  }

NewEdges <- tibble(Link = get.edge.attribute(g, "Link") ) %>%
  left_join(., predictions %>% filter(Modelname =="PF_Only")) %>%
  mutate(.fitted = ifelse(is.na(.fitted), 1e5, .fitted))

LinModLims <- set_edge_attr(g, "Link.Limit", value = NewEdges$.fitted)


SaveMultiAttacks(LinModLims, StratAttackVect, folder, TotalAttackRounds = AttackRounds, CascadeMode = T)

setwd(StratAttackWd)
folder <- "Model_PFVolt"

  if(!file.exists(folder)){
    dir.create(folder)
  }

NewEdges <- tibble(Link = get.edge.attribute(g, "Link") ) %>%
  left_join(., predictions %>% filter(Modelname =="VoltPF")) %>%
  mutate(.fitted = ifelse(is.na(.fitted), 1e5, .fitted))

LinModLims <- set_edge_attr(g, "Link.Limit", value = NewEdges$.fitted)


SaveMultiAttacks(LinModLims, StratAttackVect, folder, TotalAttackRounds = AttackRounds, CascadeMode = T)

```

##Plot differences

```{r}

RootFolder <- StratAttackWd

ExtractAttackStats(StratAttackWd, file.path(PLwd, "Attack_Strategy_SummaryData"))

AttackStratRoundData <- list.files(path = file.path(PLwd,"Attack_Strategy_SummaryData"), 
                              pattern = ".rds", 
                              full.names = TRUE) %>%
   map_df(~read_rds(.x)) %>%
        mutate(alpha = case_when(
       alpha == "Model_PF_Only"~ "PF_Model",
       alpha == "Model_PFVolt" ~ "Volt_PF_Model",
       TRUE ~ alpha)) %>%
  mutate(simulationID = case_when(
    simulationID == "1" ~"Degree" ,
    simulationID == "2" ~"EntDeg_LinkLimit",
    simulationID == "3" ~"EntDeg_PowerFlow",
    simulationID == "4" ~"Elec_Centrality",
    TRUE ~ "Centrality"
  ),
  alpha1 = alpha %>%
           str_replace_all(., "_", " ") %>%
           str_extract_all(., "([0-9])+")%>% as.numeric(.)/100,
alpha = alpha %>%
  str_replace_all(., "_", " ") %>%
  str_extract_all(., "([aA-zZ\\s])+", T) %>%
  paste0(., ifelse(is.na(alpha1), "", alpha1)),
  alpha = fct_relevel(alpha, "alpha value 5", after=2) %>%
  fct_relevel(., "alpha value 2", after=2) %>%
  fct_relevel(., "alpha value 1.5", after=2),
  PercNum = NodesAttacked/958) %>% 
  group_by(NodesAttacked, alpha) %>%
  mutate(rankblack = min_rank(-Blackout),
         rankGC = min_rank(GCfract)) %>%
  ungroup

AttackStratRoundData %>% #need to remove infinte values
  filter(alpha %in% c("alpha value 5", "Topological", "PF Model", "Real Limits")) %>%
  ggplot(aes(x = PercNum, y =  GCfract, colour = simulationID)) + 
  geom_line() +  
  #geom_line(data = RealCollapse, aes(fill = 'Real'), color = 'black') +
  #geom_line(data = ModelledCollapse, aes(fill = 'Modelled'), color = 'blue') +
  scale_fill_manual("Line Limit", values=c(1, 1)) +
  facet_wrap(~alpha) +
  scale_x_continuous(labels=scales::percent) + 
  scale_y_continuous(labels=scales::percent) +
  coord_cartesian(x = c(0,0.2)) +
  labs(title = "Change in Blackout size as nodes are attacked using multiple strategies" , 
       x = "Percent of elements attacked", 
       y = "Performance drop",
       colour = "Attack Strategy")+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
ggsave(file.path(FiguresFolder,"AttackStratDiff.pdf"))

test2 <-AttackStratRoundData %>%
  left_join(., 
            AttackStratRoundData %>%
  filter(alpha == "Real Limits") %>%
  select(NodesAttacked, simulationID, rankblack, rankGC), 
            by = c("NodesAttacked","simulationID")) %>% 
  ungroup %>%
         mutate(CorrectRank= rankblack.x==rankblack.y,
                rankdiff = rankblack.x-rankblack.y,
            r1 = as.factor(rankblack.x),
            r2= as.factor(rankblack.y)
    ) %>% ungroup

MapPairs <- expand.grid(unique(AttackStratRoundData$simulationID),unique(AttackStratRoundData$alpha) ) %>%
  as_tibble()

#calc error
test3 <- map2_df(.x= MapPairs$Var1, .y=MapPairs$Var2, ~{
  test2   %>%
    filter(alpha ==.y) %>%
    group_by(alpha) %>%
    mutate(acc = accuracy(., estimate = r1, truth =  r2) %>% pull(.estimate),
           AlphaRMSE = rmse(., estimate =rankblack.x, truth =  rankblack.y) %>% pull(.estimate)) %>%
    filter(simulationID ==.x) %>%
    group_by(simulationID, alpha) %>%
    summarise(RMSE = rmse(., estimate =rankblack.x, truth =  rankblack.y)%>% pull(.estimate), #measures for each sim ID for that class
              RSQ = rsq(., estimate =rankblack.x, truth =  rankblack.y) %>% pull(.estimate),
              CorrectRank = sum(CorrectRank, na.rm = T),
              CorrectPerc = n(),
              AlphaAccuracy = first(acc),
              AlphaRMSE = first(AlphaRMSE), #measures the whole class
              accuracy = accuracy(., estimate = r1, truth =  r2)%>% pull(.estimate)
             ) %>% 
    ungroup
          
  }) %>%
  filter(alpha!="Real Limits")
  

test2 %>%
#  filter(alpha == "alpha value 5", simulationID=="Elec_Centrality") %>%
mutate(rankdiff = rankblack.x -rankblack.y) %>%
  ggplot(.,aes(x = NodesAttacked, y = rankdiff, colour = alpha)) + geom_line() +
  labs(title= "Damage rank difference for Electrical centrality for alpha = 5\n rank difference of 0 means rank matches real results")+
  facet_wrap(simulationID ~.)


test3 %>%
  ggplot(., aes(x = simulationID, y = accuracy, fill = simulationID)) +
  geom_col() +
  facet_wrap(~alpha) +
  theme(axis.text.x = element_blank()) +
    labs(title= "The overall rank accuracy in terms of damage done\nby line limit setting and Attack strategy", 
       y = "Damage rank accuracy across entire simulation",
       x = "Attack Strategy"
      ) +
  guides(fill = guide_legend(title = "Attack Strategy"))

test <- test3 %>%
  mutate(alpha1 = alpha %>%
           str_replace_all(., "_", " ") %>%
           str_extract_all(., "([0-9\\.])+")%>% as.numeric(.))

test %>%
  group_by(alpha, alpha1) %>%
  summarise(Accuracy = first(AlphaRMSE)) %>% 
  ungroup %>%
  arrange(Accuracy)



 test %>%
  group_by(alpha, alpha1) %>%
  summarise(Accuracy = first(AlphaRMSE)) %>% #AlphaAccuracy
   ungroup %>%
   mutate(
    # alpha = ifelse(alpha == "Model PFVolt", "PF Volt Model", alpha),
     alpha = factor(alpha, levels = AlphaOrder)) %>%
  ggplot(aes(x= alpha, y = Accuracy)) +
  geom_col() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
   labs(title= "The overall strategy rank RMSE in terms of damage done by alpha level", 
       y = "Strategy damage rank RMSE across entire simulation",
       x = "Line limit settings") 
ggsave(file.path(FiguresFolder,"AttackStratRankPerf.pdf")) 
   
 #this looks like a better way of showing the data... but the simulations have different numbers of attacks so it may not be appropriate.

TempPlot<- test %>%
  group_by(alpha, alpha1) %>%
  summarise(Accuracy = first(AlphaAccuracy)) %>% #AlphaAccuracy
  ggplot(aes(x= alpha, y = Accuracy, fill = alpha1)) +
  geom_col() +
  scale_fill_gradientn(colors = c("red",   "limegreen"),
                          breaks = c(1,2,7,20,50),
                          trans = "log",
                          values = scales::rescale((c(0, 6, 7, 20, 50))))


AccBuild <- ggplot_build(TempPlot)
AccBarCol <- c(unique(AccBuild$data[[1]][[1]]), "blue")
names(AccBarCol) <-test$alpha %>%  droplevels %>% levels
rm(TempPlot)


test %>%
  ggplot(aes(x= alpha, y = RMSE, fill = alpha)) +
  geom_boxplot() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  labs(title= "The overall strategy rank RMSE in terms of damage done by alpha level", 
       y = "Strategy damage rank RMSE across entire simulation",
       x = "Line limit settings") +
  scale_fill_manual(values = AccBarCol, guide=FALSE) 

test %>% select(alpha, accuracy, RMSE) %>%group_by(alpha) %>% summarise_all(funs(mean, median)) %>% arrange(RMSE_mean)
                                       
```


###GGplot map

```{r}
GGmapData <-  MakeMapDF(g, read_csv(file.path(basewd, "point.csv")))  

#plot graph as ggplot
GGmapData %>%
  mutate(Voltage = factor(Voltage),
         PositionType = factor(PositionType),
         PositionType = fct_relevel(PositionType, "Geo Space", after = 0)) %>%
  ggplot(aes(y = Latitude, x = Longitude)) + 
  geom_line(aes(colour = Voltage, group = Link)) +
   scale_colour_brewer(palette ="Set1")+
  facet_grid(~PositionType) +
  theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank(),
        axis.title.y=element_blank(),
        axis.text.y=element_blank(),
        axis.ticks.y=element_blank()) +
  ggtitle("The UK power grid by voltage, plotted using geographic location and node space")
ggsave(file.path(FiguresFolder, "ggMapColouredEdges.pdf"))
  
```


#Tweaking the package
The below code is used to tweak the R package, add to the documentation etc, etc

```{r}
library(devtools)
library(roxygen2)
setwd( "/home/jonno/PowerGridNetworking")
document()
setwd("/home/jonno")
install("PowerGridNetworking")
detach("package:PowerGridNetworking", unload = TRUE)
library(PowerGridNetworking)

```


#Single attack exmaple

This chunk is just used so that I can have a test bed for function where I need to re-simulate an attack

```{r} 
#create graph
testg <- Proportional_Load(g, 1.5)

#get single deletion order
DeletionOrder <- DeleteOrders[1,-1] %>% t %>% .[,1]

 FixedNodes <- quo(FixedStrategyAttack(g, DeletionOrder))
    #suppres attack the grid messages
    AttackSeries <-AttackTheGrid(list(list(testg)),
                                                   FixedNodes,
                                                   referenceGrid = NULL,
                                                   MinMaxComp = 0,
                                                   TotalAttackRounds = 1000,
                                                   CascadeMode = TRUE)

  #try with much lower alpha
  AttackSeries <- read_rds(file.path("/media/jonno/Seagate Expansion Drive/ProportionalLoading/Saved_Sims/alpha_value_105", "Simulation_ID_1.rds"))

  test <- RoundTypeRemoved(AttackSeries)
  test1 <- test[[2]]

```
