---
title: "Proportional Loading"
author: "Jonathan Bourne"
date: "14 February 2018"
output: html_document
editor_options: 
  chunk_output_type: console
---





This script is for the PhD chapter/paper on proportional grid loading.

The goal of this paper is to compare real and proportional line limits and see what affect this has on cascading failures in the power-grid during attack.

Open data on powergrid modelling
https://www.sciencedirect.com/science/article/pii/S2352484716300877#f000005



LoadData2 says that all with voltage 0 are transformers. This implies they cannot be tripped and should have 1e5 as capacity

#Setup Block

```{r}

packages <- c("tidyverse", "igraph","readr","readxl", "broom", "zoo", "stringr","foreach", "doMC",  "xtable", "geomnet", "ggnetwork", "rlang", "animation", "ggridges", "poweRlaw", "Rtsne", "caret", "ranger", "xtable", "broom", "modelr", "yardstick")

new.packages <- packages[!(packages %in% installed.packages()[,"Package"])]
if(length(new.packages)) install.packages(new.packages)


sapply(packages, library, character.only = TRUE)


lapply(packages, library, character.only = TRUE)
library(PowerGridNetworking)

select <- dplyr::select

#Set up file system to read the correct folders this switches between aws and windows mode

basewd <- "/home/jonno/Dropbox/Jonathan_Bourne_Phd_Folder"
datafile <- "/home/jonno/Dropbox/Jonathan_Bourne_Phd_Folder/ETYSAppendixB"
LatexFolder <- "/home/jonno/Dropbox/Apps/ShareLaTeX/Proportional Line Limits" 
FiguresFolder <- file.path(LatexFolder, "Figures")
TablesFolder <- file.path(LatexFolder, "Tables")
MatricesFolder <- file.path(LatexFolder, "Matrices")
Functions <-"/home/jonno/Create_ETYS_network/Functions"
Tariff <- file.path(basewd,"Tariff and Transport")
PLwd <- "/media/jonno/Seagate Expansion Drive/ProportionalLoading"
Saved_Sims <- file.path(PLwd, "Saved_Sims")
#Deletion_Order_Folder <-  file.path(PLwd, "DeletionOrder") #Only one of the deletion order folders is needed. Either Nodes or Edges
Deletion_Order_Folder <- file.path(PLwd, "DeletionOrder_Nodes")
StratAttackWd <- "/media/jonno/Seagate Expansion Drive/ProportionalLoading/StratAttack"

source("/home/jonno/Create_ETYS_network/SubCode/LoadData2.R")


#FOr NetSci
#FiguresFolder <- "/home/jonno/Dropbox/Apps/ShareLaTeX/NetSci2018 Poster/Figures"
```

#Create the Attack Orders
```{r}
#Set the path to a large enough storage
setwd(PLwd)

#Ensure there is powerflow
g <- PowerFlow(gbase, "FECK40")

g %>%
  simplify(., remove.multiple = T, remove.loops = T) %>% 
    plot(.,vertex.size=.8, edge.arrow.size=.4, vertex.label=NA)

NetworkStats(g) %>%
  xtable() %>% print(type = "latex", file = file.path(FiguresFolder, "NetworkStats.txt"))

AttackRounds <- 1000

#Create a reproducible attack order
seed<- 1589
filename <- "DeleteOrders100.rds"
if(file.exists(filename)){
  DeleteOrders <- readRDS(filename)
} else {
set.seed(seed)
DeleteOrders <- MultiAttackOrder(gbase, 100)  
saveRDS(DeleteOrders, filename)
}

```

#Set alpha colour gradient
```{r}
  AlphaGrad <-scale_colour_gradientn(colors = c("red",   "limegreen"),
                          breaks = c(1,2,7,20,50),
                          trans = "log",
                          values = scales::rescale((c(0, 6, 7, 20, 50))),
                          name = expression(alpha*" level")) #"Alpha value"
```

#Comparison of line limit methods

This section compares artificial line limits created using a variety of metrics

```{r}

alpha_levels <- seq(1, 7, 0.05) #c(1, 1.05, 1.1, 1.2, 1.5, 2, 3, 5, 6,7)
#alpha_levels <- c(1, 1.05, 1.1, 1.2, 1.5, 2, 3, 5,6,7,8,9,10)

EdgeAttr <- get.edge.attribute(g) %>% names %>% 
  map(~{
    data_frame(temp = get.edge.attribute(g, name = .x)) %>%
      set_names(.x)
  }) %>% bind_cols() %>%
   filter(Link.Limit!=1e5, Voltage!=0
         )

PL_Limits <- alpha_levels %>% map(~{

  Proportional_Load(g, .x) %>% 
    get.edge.attribute(., "Link.Limit") %>%
    data_frame(temp = .) %>%
    set_names(paste0("alpha_value_", .x*100))
  
}
) %>% bind_cols() %>%
  filter(get.edge.attribute(g, "Voltage")!=0,
          get.edge.attribute(g, "Link.Limit")!= 1e5)
         
#The results

EdgeAttr2 <- PL_Limits

Limit_Method_RMSE <- EdgeAttr2 %>%
  map_df(~{
   c(postResample(.x, EdgeAttr$Link.Limit) , 
  mean(abs((EdgeAttr$Link.Limit - .x)/EdgeAttr$Link.Limit))) %>%
  matrix %>%
  t %>%
  data.frame() %>% set_names(names(postResample(EdgeAttr$Link.Limit, .x)), "MAPE" )
  
  }) %>%
  mutate(type = names(EdgeAttr2),
         method =  str_split(type, '_(?=[^_]+$)') %>% 
           transpose() %>% 
           .[[1]] %>% 
           unlist,
         Level = str_split(type, '_(?=[^_]+$)') %>% 
           transpose() %>% 
           .[[2]] %>% 
           unlist) %>%
  #This bit converts the Level to numeric. Useful when Only Alpha is being analysed
  mutate(Level = as.numeric(Level)/100)
 
Limit_Method_RMSE %>% 
ggplot(., aes(x = RMSE, y = MAPE, colour = Level)) + geom_point() +
  AlphaGrad +
  ggtitle("Error modelling line-limits using PL")
ggsave(file.path(FiguresFolder, "LimitMethodRMSE.pdf"))

Limit_Method_RMSE %>%
ggplot(., aes(x = RMSE, y = MAPE, colour = Level)) + geom_point() +
  AlphaGrad

Limit_Method_RMSE %>%
ggplot(., aes(x = MAPE, y = MAE, colour = Level)) + geom_point() +
  AlphaGrad

```

#Load level plot
```{r}

edges <- g %>% as_data_frame %>%
   mutate(alpha = Link.Limit/abs(PowerFlow),
          LoadLevel = 1/alpha,
          PercLL = percent_rank(LoadLevel),
          PercLinkLimit = percent_rank(Link.Limit),
          PercFlow = percent_rank(abs(PowerFlow)))
 
1/mean(edges$LoadLevel)
c(1.05, 1.1, 1.2, 1.5, 2, 3, 5, 6, 7, 10, 15, 20, 50)
LabelNames <- round(1/c(-.1, 0, .1,.2,.3,.4,.5,.6,.7,.8,.9,1), 2)
LabelNames[1:2] <- c("", ">10") 


ColourTypes <- data.frame(x=1:length(LabelNames[-c(1,2)]), y = LabelNames[-c(1,2)] %>% as.character %>% as.numeric())

TempPlot <- ColourTypes %>%
  ggplot(aes(x, y, colour = y)) +
  geom_point() +
  AlphaGrad

AccBuild <- ggplot_build(TempPlot)
AccBarCol <- c("blue", "blue",unique(AccBuild$data[[1]][[1]]))
names(AccBarCol) <-LabelNames %>%  as.factor %>% fct_relevel(., LabelNames) %>% levels
rm(TempPlot)

#Uses only Alpha which is much easier for people to understand
 edges %>%
   filter(is.finite(alpha), Link.Limit!= 100000) %>%
   ggplot(aes(x = LoadLevel)) + 
   geom_histogram(bins = 10, aes(y = (..count..)/sum(..count..)))+ #remove the fill to make it black again , fill = rev(AccBarCol[-c(1:2)])
  scale_y_continuous(labels = scales::percent, breaks = seq(0,.5, by= 0.05)) +
   labs(x = expression(alpha*" level"), 
        y ="Percentage of total lines", 
        title = expression("Distribution of "*alpha*" using real line limits under initial conditions"))+
 # annotate("text", x = .7, y = .2, label = "Mean Alpha = 5.4",  size=7) +#removed as can be stated in caption
   scale_x_reverse(breaks = seq(1,-.1, by=-0.1), labels= rev(LabelNames))

 # edges %>%
 #   filter(is.finite(alpha), Link.Limit!= 100000) %>%
 #   ggplot(aes(x = LoadLevel)) + geom_histogram(bins = 10, aes(y = (..count..)/sum(..count..)))+ 
 #  scale_y_continuous(labels = scales::percent, breaks = seq(0,.5, by= 0.05)) +
 #  scale_x_continuous( breaks = seq(-1,5, by=0.1), labels = scales::percent)+ 
 #   labs(x = "Load Level", y ="Percentage of total lines", title = "Distribution of Load Level using real line limits under initial conditions") +
 #    annotate("text", x = .7, y = .2, label = "Mean Load Level = 19%",  size=7)
 ggsave(file.path(FiguresFolder,"LoadLevel.pdf"))

 edges %>%
   filter(is.finite(alpha), Link.Limit!= 100000) %>%
   ggplot(aes(x = LoadLevel, colour = as.factor(Voltage))) + geom_density()
 
 edges %>%
   filter(is.finite(alpha), Link.Limit!= 100000) %>%
   summarise(meanA = mean(alpha),
             medianA = median(alpha),
             meanLL = mean(LoadLevel),
             medianLL = median(LoadLevel))
 
 median(abs(edges$Link.Limit/edges$PowerFlow))
 mean(abs(edges$Link.Limit/edges$PowerFlow))
 
 # edges %>%
 #   filter(Link.Limit != 1e5,
 #          Voltage !=0) %>%
 #   ggplot(aes(x = abs(PowerFlow), y = LoadLevel, colour = as.factor(Voltage))) +
 #   geom_point() +
 #   labs(x= "Absolute Power Flow MW", y="Load Level", title = "Relationship between power flow and Load Level", colour = "Voltage") 
 #  ggsave(file.path(FiguresFolder,"PowerFlowvsVoltage.pdf"))

 # edges %>%
 #   filter(Link.Limit != 1e5,
 #          Voltage != 0) %>%
 #   ggplot(aes(x = PercFlow, y = PercLL, colour = as.factor(Voltage))) +
 #   geom_point()

```

#Generate Attack data

##Real line limits

```{r}

setwd(Saved_Sims)

folder <- "Real_Limits"

  if(!file.exists(folder)){
    dir.create(folder)
  }

SaveMultiAttacks(g, DeleteOrders, folder, TotalAttackRounds = AttackRounds, CascadeMode = T)

```


##Infinite limits

```{r}

setwd(Saved_Sims)

folder <- "Infinite_Limits"

  if(!file.exists(folder)){
    dir.create(folder)
  }

SaveMultiAttacks(g, DeleteOrders, folder, TotalAttackRounds = AttackRounds, CascadeMode = F)

```


##PL limits

This function saves networks.
Should the function should be changed so that it can handle edges as well as nodes.

```{r}

#The vector of alpha values to be tested
#alpha_vector <- c(1.05, 1.1, 1.2, 1.5, 2, 3, 5)
setwd(Saved_Sims)
alpha_vector <- c(35)

#Create the simulations for each of the alpha avalues using 100 simulations for each
alpha_vector %>% walk(~{
  gProp <- Proportional_Load(g, alpha = .x)
  
  folder <- paste0("alpha_value_",  .x*100)
  #create folder if it doesn't already exist
  if(!file.exists(folder)){
    dir.create(folder)
  }
  
  SaveMultiAttacks(gProp, DeleteOrders, folder, TotalAttackRounds = AttackRounds, CascadeMode = T)
  
}
  
)
  
```


##Modelled limits

```{r}

#Set seed and create model input variables
set.seed(1)
ModelInputVars <- g %>% as_data_frame %>%
  mutate(absPF = abs(PowerFlow),
         Voltage = as.factor(Voltage)) %>%
  select(Link.Limit, Voltage, absPF, Link, Length)# %>%
 # mutate_if(is.numeric, funs(scale(.) %>% as.vector))

#generate k=10 crossfold validated model
models <- ModelInputVars %>%
  filter(Link.Limit != 1e5) %>%
  crossv_kfold(k = 10) %>%
  mutate(model = map(train, ~ lm(Link.Limit ~ Voltage + Length, data = .)))

#create predictions for each edge in the network
predictions <- models %>%
  unnest(map2(model, test, ~ augment(.x, newdata = .y)))

#Look at coefficiients
ModStats <- models %>%
  unnest(map(model, ~ tidy(.x))) %>%
   select(.id, term, estimate) %>%
   spread(key = term, value = estimate) %>% 
   select(-.id)
   bind_rows(ModStats %>% summarise_all(mean) %>% mutate(type = "mean"),
              ModStats %>% summarise_all(sd) %>% mutate(type = "sd")) %>%
     select(type, everything()) %>%
   #  mutate_if(is.numeric, signif, digits = 2) %>%
xtable(.,  caption = "Mean model coefficients and standard deviation across 10-fold cross-validation", label = "tab:ModCoeffs") %>%
   print(type = "latex", file = file.path(FiguresFolder, "ModCoeffs.txt"))
 
   ggplot(aes(x = term, y = estimate)) + 
   geom_boxplot()
 
 metrics(predictions ,Link.Limit, .fitted)
 #mape 
 mean(abs(predictions$.fitted-predictions$Link.Limit)/predictions$Link.Limit)
 

predictions %>%
  mutate(residual = (.fitted - Link.Limit)/Link.Limit) %>% #doesn't need to be relative. absolute gives half a random cloud
  select(Voltage, residual, absPF, Length) %>%
  ggplot(aes(log10(Length), residual)) +
  geom_point() +
  facet_wrap(~ Voltage)

#Create new edge limits using the predictions
NewEdges <- tibble(Link = get.edge.attribute(g, "Link") ) %>%
  left_join(., predictions) %>%
  mutate(.fitted = ifelse(is.na(.fitted), 1e5, .fitted))

LinModLims <- set_edge_attr(g, "Link.Limit", value = NewEdges$.fitted)

#Generate simulations
setwd(Saved_Sims)

folder <- "Linear_Model_Limits"

  if(!file.exists(folder)){
    dir.create(folder)
  }

SaveMultiAttacks(LinModLims, DeleteOrders, folder, TotalAttackRounds = AttackRounds, CascadeMode = T)

```



##Constant limits

takes the line with most power flow, adds x percent and uses that as the power limit for all line

```{r}
setwd(Saved_Sims)
#Needs to be redone as *1.05
folder <- "Constant_105"

LineLim<- max(get.edge.attribute(g, "PowerFlow"))*105

ConstantLims <- set.edge.attribute(g, "Link.Limit", value = LineLim)

  if(!file.exists(folder)){
    dir.create(folder)
  }

SaveMultiAttacks(ConstantLims, DeleteOrders, folder, TotalAttackRounds = AttackRounds, CascadeMode = T)

```


##Constant voltage limits

```{r}
setwd(Saved_Sims)

folder <- "Constant_Volt_105"


Const_Volt <- EdgeAttr %>%
    group_by(Voltage) %>%
  mutate(constant = max(PowerFlow)*1.05) %>%
    ungroup %>%
  select(constant)

LineLim<- Const_Volt$constant

ConstantLims <- set.edge.attribute(g, "Link.Limit", value = LineLim)

  if(!file.exists(folder)){
    dir.create(folder)
  }

SaveMultiAttacks(ConstantLims, DeleteOrders, folder, TotalAttackRounds = AttackRounds, CascadeMode = T)

```



##Extend the experiment
This is used to extend the original experiment from 150 node removals to complete collapse.
The whole experiment has been updated so this code chunk is no longer useful.
It is kept in for completness
```{r}
 
# setwd(PLwd)
# directories <- list.dirs()
# 
# directories[grepl("value_",directories)][-c(1,2,3,4,5,6)] %>% 
#   walk(~{
#     setwd(file.path(PLwd, .x))
#     print(.x)
#     ExtendMulltiAttack(list.files(), DeleteOrders)
#     gc()
#   }
# )


```


#Extracting stats

Extracting stats is slow this extracts the stats and saves them as a file.

```{r}

ExtractAttackStats(Saved_Sims, file.path(PLwd, "SummaryData"))

#Load the saved files
AttackRoundData <- list.files(path = file.path(PLwd,"SummaryData"), 
                              pattern = ".rds", 
                              full.names = TRUE) %>%
   map_df(~read_rds(.x))



```


#Construct attack summaries

Plots simple graphs from summary data

```{r}

SummariseMonteCarlo <- function(df){
 df %>% 
    mutate(PGfract = (max(PowerGen)- PowerGen)/max(PowerGen)) %>%
    group_by(NodesAttacked, alpha) %>%
    summarise(mean = mean(GCfract),
              sd = sd(GCfract),
              GC95 = quantile(GCfract, .95),
              GC05 = quantile(GCfract, .05),
              count = n(),
              mPGfract = mean(PGfract),
              sdPGfract = sd(PGfract),
              medPGfract = median(PGfract),
              PG95 = quantile(PGfract, .95),
              PG05 = quantile(PGfract, .05),
              PGmax = max(PGfract),
              PGmin = min(PGfract),
              mLoad = mean(GridLoading, na.rm = T),
              GL95 = quantile(GridLoading, .95, na.rm = T),
              GL05 = quantile(GridLoading, .05, na.rm = T)) %>%
    ungroup %>%
    group_by(alpha) %>%
     mutate(ID =n():1) %>%
    ungroup
  
}

SummaryofGC<- AttackRoundData %>%
  SummariseMonteCarlo %>%
  mutate(PercNum = NodesAttacked/958,
         alpha = sub("alpha_value_", "", alpha) %>% sub("_", " ", .))


PNodeDens <-  AttackRoundData %>%
  mutate(PercNum = round(NodesAttacked*100/958),
            LoadDrop = (first(GridLoading)-GridLoading)/first(GridLoading))


# test2 <- PNodeDens  %>%
#   select(GCfract, Blackout, alpha, PercNum) %>%
#   gather(., key="Type", value = "value",GCfract, Blackout) %>%
#   mutate(Type = ifelse(Type == "GCfract","Giant componant size reduction", "Blackout size"))
#   
# 
#  test2   %>%
#      filter(is.finite(value)) %>%
#   mutate(  PercAttacked= fct_rev(as_factor(paste0(PercNum, "%"))))  %>%
#   ggplot(aes(y = PercAttacked)) +
#   geom_density_ridges(aes(x = value, fill = alpha), alpha = 0.5)  + 
#   scale_x_continuous(labels=scales::percent)  +
#       facet_grid(~Type) +
#   labs(x = "Performance drop", y = "Percent of elements attacked",
#        title = "Change in the performance distribution as number of attacks increase") 


 NodeCollapse <- rbind(SummaryofGC %>%
  select(PercNum, mean, alpha, GC05, GC95, sd) %>% mutate(type = "Giant componant size reduction"),
SummaryofGC %>% 
  select(PercNum, mPGfract, alpha, PG05, PG95, sdPGfract) %>% 
  mutate(type = "Blackout size") %>%
  rename(mean = mPGfract, GC05 = PG05, GC95 = PG95, sd = sdPGfract)
) %>% mutate(Target = "Node") %>%
   filter(alpha != "Constant 105", alpha != "Constant Volt_105" )

 NodeCollapse2<- NodeCollapse %>%
   filter(alpha != "Real Limits", alpha != "Linear Model_Limits") %>%
   mutate(alpha = ifelse(alpha == "Infinite Limits", "Inf", alpha),
          alpha = as.numeric(alpha)/100) %>%
   arrange(alpha)
 
AlphaCollapse <- NodeCollapse2 %>%
       filter(is.finite(sd))#need to remove infinte values 

RealCollapse <- NodeCollapse %>% 
               filter(alpha == "Real Limits",is.finite(sd))#need to remove infinte values 
   
ModelledCollapse <- NodeCollapse %>% 
               filter(alpha == "Linear Model_Limits",is.finite(sd))#need to remove infinte values 

NameOrder <- tibble(name = c("Real", "Modelled"), Colour = c("black", "blue")) %>% arrange(name)

AlphaCollapse %>% #need to remove infinte values 
  ggplot(aes(x = PercNum, y =  mean, group = alpha)) + 
  geom_line(aes(colour = as.numeric(alpha)), show.legend = TRUE) +  
  AlphaGrad +
  geom_line(data = RealCollapse, aes(fill = 'Real'), color = 'black', linetype ="longdash") +
  geom_line(data = ModelledCollapse, aes(fill = 'Modelled'), color = 'blue', linetype ="twodash") +
  scale_fill_manual("Line Limit", values=c(1, 1),
        guide=guide_legend(override.aes = list(colour=NameOrder$Colour))) +
  facet_grid(~type) +
  scale_x_continuous(labels=scales::percent) + 
  scale_y_continuous(labels=scales::percent) +
  coord_cartesian(x = c(0,0.5)) +
  labs(title = "Change in Giant componant and Blackout size as nodes are attacked" , 
       x = "Percent of elements attacked", 
       y = "Performance drop")
 
 ggsave(file.path(FiguresFolder,"GCandBlackoutChange.pdf"))


 AlphaCollapse %>% #need to remove infinte values 
  ggplot(aes(x = PercNum, y =  sd, group = alpha)) + 
  geom_line(aes(colour = as.numeric(alpha)), show.legend = TRUE) +  
  AlphaGrad +
  geom_line(data = RealCollapse, aes(fill = 'Real'), color = 'black', linetype ="longdash") +
  geom_line(data = ModelledCollapse, aes(fill = 'Modelled'), color = 'blue', linetype ="twodash")  +
  scale_fill_manual("Line Limit", values=c(1, 1),
        guide=guide_legend(override.aes = list(colour=NameOrder$Colour))) +
  facet_grid(~type) +
  scale_x_continuous(labels=scales::percent) + 
  scale_y_continuous(labels=scales::percent) +
  coord_cartesian(x = c(0,0.5))  +
  labs(title = "Standard deviation of damage across all simulations" , x = "Percent of elements attacked", y = "Standard deviation of damage")
 ggsave(file.path(FiguresFolder,"SDchange.pdf"))
 
 
 NodeCollapse3 <- bind_rows(AlphaCollapse %>% mutate(alpha = as.character(alpha)), ModelledCollapse) %>%
   left_join(., select(RealCollapse, PercNum, Realmean = mean, Realsd = sd , type) , by = c("PercNum", "type"))
   
 Inputs <- expand.grid(unique(NodeCollapse3$alpha), unique(NodeCollapse3$type)) 
  
MeanRMSE <- map2_df(.x = Inputs$Var1, .y = Inputs$Var2,~{
    NodeCollapse3 %>%
      filter(alpha == .x, type == .y) %>%
     metrics(Realmean, mean) %>%
     mutate(alpha = .x, type = .y)
  } ) %>%
  select(-rsq) %>%
  spread(key = type, value = rmse)

Meansd <- map2_df(.x = Inputs$Var1, .y = Inputs$Var2,~{
    NodeCollapse3 %>%
      filter(alpha == .x, type == .y) %>%
     metrics(Realsd, sd) %>%
     mutate(alpha = .x, type = .y)
  } ) %>%
  select(-rsq) %>%
  spread(key = type, value = rmse)

 
```


#Deletion similarity

##Round Deleted

Get the round number that an edge was deleted.

```{r}

FolderVect <- list.files(path = Saved_Sims) #folder where all the alpha FOLDERS are
FileVect <- list.files(path = Deletion_Order_Folder) %>% gsub(".rds", "",.) #folder where all the deletion order FILES are
new.type <- FolderVect[!(FolderVect %in% FileVect)] #The FOLDERS that are not present as FILES
TargetType <- "Node" #Either Node or Edge depending on which deletion order is being used

if(length(new.type)>0){
file.path(Saved_Sims, new.type) %>%
  walk( ~{
    print(.x) #print name of folder where deletion order will be calculated
    
  Removeddf <- list.files(path = .x, full.names = TRUE) %>% #list the different network of network rds files present
    map_df(~{
        file <- .x
        print(file)
        read_rds(file) %>%
          RoundRemoved(type = TargetType)  %>%
          mutate(Sim = gsub(".rds", "",file) %>% basename)
      }
    ) %>%
    group_by(Sim) %>%
    mutate(RoundRemoved = ifelse(is.na(RoundRemoved), max(RoundRemoved), RoundRemoved),
         alpha = basename(.x)) %>% 
    ungroup

  Removeddf %>%
        write_rds(x = ., paste0(file.path(Deletion_Order_Folder,basename(.x)), ".rds"))
  }
  )

} 
  
AllRemovedEdges <- list.files(Deletion_Order_Folder, full.names = TRUE) %>%
  map_df(~read_rds(.x))


CleanNames <- function(df, TargetColumn, AlphaOrder){
temp <- df  %>%
  mutate_(temp1 = TargetColumn) %>%
 mutate(temp2 = temp1,
          temp2 = temp1 %>%
           str_replace_all(., "_", " ") %>%
           str_extract_all(., "([0-9])+")%>% as.numeric(.)/100,
temp3 = temp1 %>%
  str_replace_all(., "_", " ") %>%
  str_extract_all(., "([aA-zZ\\s])+", T) %>%
  paste0(., ifelse(is.na(temp2), "", temp2)),
        temp3 = temp3 %>% as.factor() %>%
  fct_relevel(., AlphaOrder)
) %>%
  select(temp3)
temp <-temp  %>% set_names(paste0(TargetColumn,"2")) 
 
temp <- bind_cols(df, temp)
return(temp)
}

```

##Number of round per line-type
```{r}

#Check number of rounds
 test <- AllRemovedEdges %>%
  group_by(Sim, alpha) %>%
  summarise(rounds = max(RoundRemoved, na.rm = T)) %>%
   ungroup

 
 #Plot the number of rounds
test %>%  CleanNames(., "alpha", AlphaOrder) %>%
  mutate( alpha = ifelse(alpha== "Infinite_Limits","Inf", alpha),
         alpha = gsub("alpha_value_", "", alpha),
         alpha = as.numeric(alpha)/100
) %>%
  ggplot(aes(x = alpha2, y = rounds)) + geom_boxplot()+
    theme(legend.position = "none", 
        axis.text.x = element_text(angle = 45, hjust = 1)) 

test2 <- AllRemovedEdges %>%
  group_by(Sim, alpha) %>%
  mutate(decile = ntile(RoundRemoved, 10))

```


##Plot Correlation

```{r}
# testList <- file.path("/media/jonno/Seagate Expansion Drive/ProportionalLoading/Saved_Sims/Linear_Model_Limits",
#                   "Simulation_ID_1.rds") %>% 
#   read_rds

#Get only the real limits
RealPreCor  <- AllRemovedEdges %>%
  filter(alpha == "Real_Limits") %>%
  select(-alpha)

#Add the real limits onto the other nodes to allow direct comparison
#Filter out the NA values
PreCorRemoved  <- AllRemovedEdges %>%
  filter(alpha != "Real_Limits") %>%
  left_join(., RealPreCor, by = c("Edges", "Sim")) %>%
  mutate(RoundRemoved.x = ifelse(TargetNode.x, NA, RoundRemoved.x ),
         RoundRemoved.y = ifelse(TargetNode.y, NA, RoundRemoved.y ))


AllCombos <- PreCorRemoved  %>% distinct(alpha, Sim)

#Cycle through all the combinations of alpha and sim to get the corellation for all
  test <- map2_df(.x = AllCombos$Sim, .y = AllCombos$alpha, ~{
   
    temp <- PreCorRemoved %>%
    filter(Sim == .x, alpha == .y, complete.cases(.))
      cor(temp$RoundRemoved.x, temp$RoundRemoved.y, method = "kendall") %>%
        tibble(Sim = .x, alpha = .y, cor =.)
    
  })

#"Infinite Limits"
AlphaOrder <- c("alpha value 1","alpha value 1.05","alpha value 1.1","alpha value 1.2","alpha value 1.5","alpha value 2" ,"alpha value 3","alpha value 5","alpha value 6","alpha value 7","alpha value 10","alpha value 15","alpha value 20","alpha value 50","Infinite Limits" ,"Linear Model Limits")  

#Pre process data for plot
 AlphavsCor <- test %>%  CleanNames(., "alpha", AlphaOrder) %>%
  mutate( alpha = ifelse(alpha== "Infinite_Limits","Inf", alpha),
         alpha = gsub("alpha_value_", "", alpha),
         alpha = as.numeric(alpha)/100
) 
 
 #Make temporary plot
 #This is used so that the blue can be added on for the linear line limits
 TempPlot <- AlphavsCor %>%
  ggplot(aes(x = alpha2, y = cor, fill = alpha)) + geom_boxplot()+
  scale_fill_gradientn(colors = c("red",   "limegreen"),
                          breaks = c(1,2,7,20,50),
                          trans = "log",
                          values = scales::rescale((c(0, 6, 7, 20, 50))))

#Extract the colour codes from the ggplot object.
AccBuild <- ggplot_build(TempPlot)
AccBarCol <- c(unique(AccBuild$data[[1]][[1]]), "blue")
names(AccBarCol) <-AlphavsCor$alpha2 %>%  levels
rm(TempPlot)

AlphavsCor %>%
    ggplot(aes(x= alpha2, y = cor, fill = alpha2)) +
  geom_boxplot() +
    scale_fill_manual(values= AccBarCol) +
  scale_y_continuous( breaks = seq(0,1, by= 0.1)) +
  theme(legend.position = "none", 
        axis.text.x = element_text(angle = 45, hjust = 1)) +
  labs(x = expression(alpha*" level"), y ="Correlation with real line limits", title= "Node removal rank correlation against real limits")

ggsave(file.path(FiguresFolder, "CorBoxPlot.pdf"))

AlphavsCor %>% 
  group_by(alpha) %>%
  summarise(mean= mean(cor),
            median = median(cor),
            sd = sd(cor))


#Check the number of NA values
#Na values arethe nodes that were targeted for removal. They are therefore removed from the simulation
HowManyNAs <- PreCorRemoved %>%
  group_by(alpha, Sim) %>%
  summarise(counts = sum(is.na(RoundRemoved.x*RoundRemoved.y)))

HowManyNAs %>%
  ggplot(aes(x = as.factor(alpha), y = counts)) + geom_boxplot()


```


#Damage analysis
This chunk produces Boxplots of the evaluation metrics for each simulation type.
It isn't hugley interesting so isn't included.

```{r}
#compares the damge of each line limit to the real damage using several metrics
DamageComparison <- function(df, Target = "Blackout"){
  
 df <- df %>% rename_(Target = Target)
  
  1:100 %>% map_df(~{

SimAttack <- df %>%
  filter(simulationID == .x) %>%
  select(Target, alpha, NodesAttacked) %>% 
  spread(key = alpha, value = Target) %>%
   select(-NodesAttacked) %>%
  filter(Real_Limits !=1)

SimAttack[is.na(SimAttack)] <- 1
  
  test2 <- SimAttack %>% map_df(~{
   c(postResample(.x, SimAttack$Real_Limits) , 
  mean(abs((SimAttack$Real_Limits - .x)/SimAttack$Real_Limits), na.rm = T)
  ) %>%
  matrix %>%
  t %>%
  data.frame() %>% 
      set_names(names(postResample(SimAttack$Real_Limits, .x)), "MAPE" )
}
) %>% mutate(type = names(SimAttack),
             SimulationID = .x)

}) %>% 
  rename(alpha  = type) %>%
  filter(alpha != "Real_Limits") %>%
    # mutate(alpha = ifelse(alpha== "Infinite_Limits","Inf", alpha),
    #      alpha = gsub("alpha_value_", "", alpha),
    #      alpha = as.numeric(alpha)/100) 
      CleanNames(., "alpha", AlphaOrder) 
}

#Sets up the plot for comparing different metrics, the metric of choice info is then added on

BasePlot <- function(df){

  df %>%
    ggplot(aes(x= alpha2, fill = alpha2)) +
    theme(legend.position = "none",  
        axis.text.x = element_text(angle = 45, hjust = 1))+
    scale_fill_manual(values= AccBarCol) + #requires the colours that have been previously calculated in the boxplot chunk
  scale_y_continuous( breaks = seq(0,1, by= 0.1))
  
  }

AccuracyAnalysis <- DamageComparison(AttackRoundData, "Blackout")

AccuracyAnalysis %>%
  select(-SimulationID,-alpha) %>%
  group_by(alpha2) %>%
  summarise_all(funs(mean, median))

AccPlot <- AccuracyAnalysis  %>% BasePlot

 AccPlot + geom_boxplot(aes(y = RMSE)) +
  labs(x = expression(alpha*" level"), 
       title = expression("RMSE against real line limits for all calculated "*alpha*" levels") )
ggsave(file.path(FiguresFolder, "RMSEChange.pdf"))


AccPlot + geom_boxplot(aes(y = Rsquared)) +
  labs(x = "alpha", title = "Rsquared against real line limits as alpha increases") 

AccPlot + geom_boxplot(aes(y = MAE)) +
  labs(x = "alpha", title = "MAE against real line limits as alpha increases") 

AccPlot + geom_boxplot(aes(y = log(MAPE))) +
  labs(x = "alpha", title = "MAPE agtest %>%
  group_by(alpha, alpha1) %>%
  summarise(Accuracy = first(AlphaAccuracy)) %>% #AlphaAccuracy
  ggplot(aes(x= alpha, y = Accuracy, fill = alpha)) +
  geom_col() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  labs(title= "The overall rank accuracy in terms of damage done by alpha level", 
       y = "Damage rank accuracy across entire simulation",
       x = "Line limit settings") +
ainst real line limits as alpha increases") 


#Analysis for giant component size

AccuracyAnalysisGC <- DamageComparison(AttackRoundData, "GCfract")

AccuracyAnalysisGC %>%
  select(-SimulationID,-alpha) %>%
  group_by(alpha2) %>%
  summarise_all(funs(mean, median), na.rm = T)

# AccuracyAnalysisGC %>% BasePlot + geom_boxplot(aes(y = RMSE)) +
#   labs(x = "alpha", title = "GCfract RMSE against real line limits as alpha increases") 
# ggsave(file.path(FiguresFolder, "RMSEChangeGCfract.pdf"))


```


#Strategy difference

See the difference between strategies

```{r}

ElecCen1<- ElectricalCentrality(g)

StratAttackVect <- c(as_data_frame(g, what = "vertices") %>% 
  as_tibble %>%
      mutate(metric = degree(g)) %>%
      arrange(desc(metric)) %>% .$name,

as_data_frame(g, what = "vertices") %>%
      mutate(metric = EntropicDegree(g, Scale = TRUE)) %>%
      arrange(desc(metric)) %>% .$name,

as_data_frame(g, what = "vertices") %>%
      mutate(metric = EntropicDegree(g, value = "PowerFlow", Scale = TRUE)) %>%
      arrange(desc(metric)) %>% .$name,


ElecCen1$NodeEC %>% arrange(-NodeEC) %>% .$Bus.Name,

 as_data_frame(g, what = "vertices") %>%
      mutate(metric = betweenness(g)) %>%
      arrange(desc(metric)) %>% .$name
) %>% matrix(., nrow = 5, byrow = T) %>%
  as_tibble %>%
  mutate(SimulationID = paste0("Simulation_ID_",1:5)) %>%
  select(SimulationID, everything()) %>%
  setNames(c("SimulationID", paste0("Target", 1:958)))


 
```


##Different strategies 1 load level
```{r}
#The vector of alpha values to be tested
alpha_vector <- c(1.05, 1.1,1.5, 2, 5,  10, 20, 50)

setwd(StratAttackWd)

#Create the simulations for each of the alpha avalues using 100 simulations for each
alpha_vector %>% walk(~{
  gProp <- Proportional_Load(g, alpha = .x)
  
  folder <- paste0("alpha_value_",  .x*100)
  #create folder if it doesn't already exist
  if(!file.exists(folder)){
    dir.create(folder)
  }
  
  SaveMultiAttacks(gProp, StratAttackVect, folder, TotalAttackRounds = AttackRounds, CascadeMode = T)
  
}
  
)

setwd(StratAttackWd)
folder <- "Real_Limits"

  if(!file.exists(folder)){
    dir.create(folder)
  }

SaveMultiAttacks(g,  StratAttackVect, folder, TotalAttackRounds = AttackRounds, CascadeMode = T)

setwd(StratAttackWd)
folder <- "Infinite_Limits"

  if(!file.exists(folder)){
    dir.create(folder)
  }

SaveMultiAttacks(g, StratAttackVect, folder, TotalAttackRounds = AttackRounds, CascadeMode = F)

setwd(StratAttackWd)
folder <- "Linear_Model_Limits"

  if(!file.exists(folder)){
    dir.create(folder)
  }

SaveMultiAttacks(LinModLims, StratAttackVect, folder, TotalAttackRounds = AttackRounds, CascadeMode = T)

```

##Plot differences

```{r}

RootFolder <- StratAttackWd

ExtractAttackStats(StratAttackWd, file.path(PLwd, "Attack_Strategy_SummaryData"))

AttackStratRoundData <- list.files(path = file.path(PLwd,"Attack_Strategy_SummaryData"), 
                              pattern = ".rds", 
                              full.names = TRUE) %>%
   map_df(~read_rds(.x)) %>%
  mutate(simulationID = case_when(
    simulationID == "1" ~"Degree" ,
    simulationID == "2" ~"EntDeg_LinkLimit",
    simulationID == "3" ~"EntDeg_PowerFlow",
    simulationID == "4" ~"Elec_Centrality",
    TRUE ~ "Centrality"
  ),
  alpha1 = alpha %>%
           str_replace_all(., "_", " ") %>%
           str_extract_all(., "([0-9])+")%>% as.numeric(.)/100,
alpha = alpha %>%
  str_replace_all(., "_", " ") %>%
  str_extract_all(., "([aA-zZ\\s])+", T) %>%
  paste0(., ifelse(is.na(alpha1), "", alpha1)),
  alpha = fct_relevel(alpha, "alpha value 5", after=2) %>%
  fct_relevel(., "alpha value 2", after=2) %>%
  fct_relevel(., "alpha value 1.5", after=2),
  PercNum = NodesAttacked/958) %>% 
  group_by(NodesAttacked, alpha) %>%
  mutate(rankblack = min_rank(-Blackout),
         rankGC = min_rank(GCfract)) %>%
  ungroup

AttackStratRoundData %>% #need to remove infinte values
  filter(alpha %in% c("alpha value 5", "Infinite Limits", "Linear Model Limits", "Real Limits")) %>%
  ggplot(aes(x = PercNum, y =  GCfract, colour = simulationID)) + 
  geom_line() +  
  #geom_line(data = RealCollapse, aes(fill = 'Real'), color = 'black') +
  #geom_line(data = ModelledCollapse, aes(fill = 'Modelled'), color = 'blue') +
  scale_fill_manual("Line Limit", values=c(1, 1)) +
  facet_wrap(~alpha) +
  scale_x_continuous(labels=scales::percent) + 
  scale_y_continuous(labels=scales::percent) +
  coord_cartesian(x = c(0,0.4)) +
  labs(title = "Change in Blackout size as nodes are attacked using multiple strategies" , 
       x = "Percent of elements attacked", 
       y = "Performance drop",
       colour = "Attack Strategy")+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
ggsave(file.path(FiguresFolder,"AttackStratDiff.pdf"))

test2 <-AttackStratRoundData %>%
  left_join(., 
            AttackStratRoundData %>%
  filter(alpha == "Real Limits") %>%
  select(NodesAttacked, simulationID, rankblack, rankGC), 
            by = c("NodesAttacked","simulationID")) %>% 
  ungroup %>%
         mutate(CorrectRank= rankblack.x==rankblack.y,
                rankdiff = rankblack.x-rankblack.y,
            r1 = as.factor(rankblack.x),
            r2= as.factor(rankblack.y)
    ) %>% ungroup

MapPairs <- expand.grid(unique(test2$simulationID),unique(test2$alpha) ) %>%
  as_tibble()

#calc error
test3 <- map2_df(.x= MapPairs$Var1, .y=MapPairs$Var2, ~{
  test2   %>%
    filter(alpha ==.y) %>%
    group_by(alpha) %>%
    mutate(acc = accuracy(., estimate = r1, truth =  r2),
           AlphaRMSE = rmse(., estimate =rankblack.x, truth =  rankblack.y)) %>%
    filter(simulationID ==.x) %>%
    group_by(simulationID, alpha) %>%
    summarise(RMSE = rmse(., estimate =rankblack.x, truth =  rankblack.y), #measures for each sim ID for that class
              RSQ = rsq(., estimate =rankblack.x, truth =  rankblack.y),
              CorrectRank = sum(CorrectRank, na.rm = T),
              CorrectPerc = n(),
              AlphaAccuracy = first(acc),
              AlphaRMSE = first(AlphaRMSE), #measures the whole class
              accuracy = accuracy(., estimate = r1, truth =  r2)
             ) %>% 
    ungroup
          
  }) %>%
  filter(alpha!="Real Limits")
  

test2 %>%
  filter(alpha == "alpha value 5", simulationID=="Elec_Centrality") %>%
mutate(rankdiff = rankblack.x -rankblack.y) %>%
  ggplot(.,aes(x = NodesAttacked, y = rankdiff)) + geom_line() +
  labs(title= "Damage rank difference for Electrical centrality for alpha = 5\n rank difference of 0 means rank matches real results")


test3 %>%
  ggplot(., aes(x = simulationID, y = accuracy, fill = simulationID)) +
  geom_col() +
  facet_wrap(~alpha) +
  theme(axis.text.x = element_blank()) +
    labs(title= "The overall rank accuracy in terms of damage done\nby line limit setting and Attack strategy", 
       y = "Damage rank accuracy across entire simulation",
       x = "Attack Strategy"
      ) +
  guides(fill = guide_legend(title = "Attack Strategy"))

test <- test3 %>%
  mutate(alpha1 = alpha %>%
           str_replace_all(., "_", " ") %>%
           str_extract_all(., "([0-9\\.])+")%>% as.numeric(.))

TempPlot<- test %>%
  group_by(alpha, alpha1) %>%
  summarise(Accuracy = first(AlphaAccuracy)) %>% #AlphaAccuracy
  ggplot(aes(x= alpha, y = Accuracy, fill = alpha1)) +
  geom_col() +
  scale_fill_gradientn(colors = c("red",   "limegreen"),
                          breaks = c(1,2,7,20,50),
                          trans = "log",
                          values = scales::rescale((c(0, 6, 7, 20, 50))))


AccBuild <- ggplot_build(TempPlot)
AccBarCol <- c(unique(AccBuild$data[[1]][[1]]), "blue")
names(AccBarCol) <-test$alpha %>%  droplevels %>% levels
rm(TempPlot)

 test %>%
  group_by(alpha, alpha1) %>%
  summarise(Accuracy = first(AlphaRMSE)) %>% #AlphaAccuracy
  ggplot(aes(x= alpha, y = Accuracy)) +
  geom_col() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  labs(title= "The overall rank RMSE in terms of damage done by alpha level", 
       y = "Damage rank RMSE across entire simulation",
       x = "Line limit settings") #+
#  scale_fill_manual(values = AccBarCol, guide=FALSE) 
ggsave(file.path(FiguresFolder,"AttackStratRankPerf.pdf")) 
   
 #this looks like a better way of showing the data... but the simulations have different numbers of attacks so it may not be appropriate.
test %>%
  ggplot(aes(x= alpha, y = RMSE, fill = alpha)) +
  geom_boxplot() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  labs(title= "The overall rank RMSE in terms of damage done by alpha level", 
       y = "Damage rank RMSE across entire simulation",
       x = "Line limit settings") +
  scale_fill_manual(values = AccBarCol, guide=FALSE) 

test %>% select(alpha, accuracy, RMSE) %>%group_by(alpha) %>% summarise_all(funs(mean, median))
                                       
```


#Geo Points

```{r}

library(geosphere)

points <- read_csv("/home/jonno/Downloads/point.csv")

points <- get.vertex.attribute(gbase, "name") %>% tibble(name = .) %>%
  left_join(., points, by = c("name" = "Edges")) %>%
  group_by(name) %>%
  mutate(counts = n()) %>%
  ungroup %>%
  slice(-219) %>%
  mutate(Lat = ifelse(name == "TILB40" ,51.46006, Lat))

NApoints <-points %>%
  filter(is.na(Lon)) %>%
  pull(name)

g2 <- set.vertex.attribute(gbase, "Lat", value = points$Lat) %>%
  set.vertex.attribute(., "Lon",value =  points$Lon)

AllPoints <- ego(g2, nodes = NApoints) %>% map_df(~{
  
 points %>%
    filter(name %in% names(.x)) %>%
    summarise(Lon = mean(Lon, na.rm = T),
              Lat = mean(Lat, na.rm = T))
  
})
```


##Check Geopoints

Some of the geopoints are not in the right location. Here I check the lat long distance with the distance provided by dataset

```{r}

TempPoints <- points %>%
select(name, Lat, Lon) 

CableTest <- trans2 %>%
    mutate( Length = OHL.Length + Cable.Length ) %>%
  select(Bus.1, Bus.2, Length) %>%
  left_join(., TempPoints, by = c("Bus.1"= "name")) %>%
    left_join(., TempPoints, by = c("Bus.2"= "name")) 


test <- 1:nrow(CableTest) %>%
  map_df(~{
    CableTest[.x,] %>%
      mutate(geodist = distm(as.matrix(data_frame(Lon.x, Lat.x)), 
                         as.matrix(data_frame(Lon.y, Lat.y)))/1000) #intometers
    
  }) %>%
  mutate(geodist = round(geodist, 2),
         diff = Length - geodist,
         absdiff = abs(diff),
         ratio = absdiff/Length)


postResample(test$Length, test$geodist)

rm(TempPoints)

table(CableTest$Length==0)



```


##Map Geo points to UK regions
```{r}


#Map to regions of UK

ShapeFolder <- "/home/jonno/Dropbox/SSE/Empty Homes/ShapeFiles/Local_Authority_Districts_December_2014_Ultra_Generalised_Clipped_Boundaries_in_Great_Britain"

library(sf)
library(rgdal)
library(RColorBrewer)
UKLADS <- readOGR(file.path(ShapeFolder, "Local_Authority_Districts_December_2014_Ultra_Generalised_Clipped_Boundaries_in_Great_Britain.shp"))
Regions <- read_csv(file.path("/home/jonno/Dropbox/MScThesis", "Local_Authority_District_to_Region_December_2017_Lookup_in_England_.csv"))
  
g3 <- set.vertex.attribute(g2, "Lat", index = NApoints, value = AllPoints$Lat) %>%
  set.vertex.attribute(., "Lon",index = NApoints, value = AllPoints$Lon)

Positioning <- matrix(c(get.vertex.attribute(g3, "Lon"),
                        get.vertex.attribute(g3, "Lat")),
                      ncol = 2)

g3 %>%
  simplify(., remove.multiple = T, remove.loops = T) %>% 
    plot(.,vertex.size=.8, edge.arrow.size=.4, vertex.label=NA, layout = Positioning)


test <- Positioning %>% as.tibble %>%
  rename(Longitude = V1, Latitude = V2)

# Assignment modified according
coordinates(test) <- ~ Longitude + Latitude

#After you create your list of latlongs you must set the proj4string to longlat
proj4string(test) <- CRS("+proj=longlat")

#Before you re-set the proj4string to the one from sodo you must actually convert #your coordinates to the new projection
test <- spTransform(test, proj4string(UKLADS))

# Set the projection of the SpatialPointsDataFrame using the projection of the shapefile
proj4string(test) <- proj4string(UKLADS)

ColourLegend<- tibble(RGN17NM = c(unique(Regions$RGN17NM), "Scotland", "Wales"), colours = brewer.pal(11, "Paired"))

#create colours for vertices
test2 <- over(test, UKLADS) %>%
  left_join(., Regions, by = c("lad14cd"="LAD17CD")) %>%
  mutate(RGN17NM = ifelse(grepl("W",lad14cd),"Wales", RGN17NM),
         RGN17NM = ifelse(grepl("S",lad14cd),"Scotland", RGN17NM)) %>%
  left_join(., ColourLegend)


#add vertex colours to graph
g4 <- set.vertex.attribute(g3, "Region", value = test2$RGN17NM) %>%
  set.vertex.attribute(., "color", value = test2$colours)
#plot graph in geospace side by side with graph in graph space
par(mfrow=c(1,2), mar=rep(1,4))
g4 %>% 
  simplify(., remove.multiple = T, remove.loops = T) %>% 
    plot(.,vertex.size=4, vertex.label=NA, layout = Positioning)
g4 %>% 
  simplify(., remove.multiple = T, remove.loops = T) %>% 
    plot(.,vertex.size=3, vertex.label=NA)


#Colour graph edges

#take the base graph and rename
g5 <- g3

VoltageColours <- data_frame(Voltage = c(0, 132, 275, 400), colour = brewer.pal(4, "Set1"))

for (i in 1:4){
  
  E(g5)$color[E(g5)$Voltage == VoltageColours$Voltage[i]] <- VoltageColours$colour[i]
  
}


pdf(file.path(FiguresFolder,"MapColouredEdges.pdf"))
oldpar <- par(mfrow=c(1,2), mar=c(3,3,1,1), oma=c(0,0,3,1))  
g5 %>% 
  simplify(., remove.multiple = T, remove.loops = T) %>% 
    plot(.,vertex.size=1, edge.width = 2, vertex.label=NA, layout = Positioning, edge.color = E(g5)$color)
g5 %>% 
  simplify(., remove.multiple = T, remove.loops = T) %>% 
    plot(.,vertex.size=1, edge.width = 2, vertex.label=NA, edge.color = E(g5)$color)
mtext("Line voltage in UK power grid", side=3, line=1, outer=TRUE, cex=2, font=2)
par(oldpar)
dev.off()

```


#Tweaking the package
The below code is used to tweak the R package, add to the documentation etc, etc

```{r}
library(devtools)
library(roxygen2)
setwd( "/home/jonno/PowerGridNetworking")
document()
setwd("/home/jonno")
install("PowerGridNetworking")
library(PowerGridNetworking)

```

