---
title: "Proportional Loading"
author: "Jonathan Bourne"
date: "14 February 2018"
output: html_document
editor_options: 
  chunk_output_type: console
---

This script is for the PhD chapter/paper on proportional grid loading.

The goal of this paper is to compare real and proportional line limits and see what affect this has on cascading failures in the power-grid during attack.

#Setup Block


```{r}
packages <- c("tidyverse", "igraph","readr","readxl", "broom", "zoo", "stringr","foreach", "doMC",  "xtable", "geomnet", "ggnetwork", "rlang", "animation", "ggridges", "poweRlaw")

new.packages <- packages[!(packages %in% installed.packages()[,"Package"])]
if(length(new.packages)) install.packages(new.packages)


lapply(packages, library, character.only = TRUE)
library(PowerGridNetworking)

select <- dplyr::select

#Set up file system to read the correct folders this switches between aws and windows mode

basewd <- "/home/jonno/Dropbox/Jonathan_Bourne_Phd_Folder"
datafile <- "/home/jonno/Dropbox/Jonathan_Bourne_Phd_Folder/ETYSAppendixB"
LatexFolder <- "/home/jonno/Dropbox/Apps/ShareLaTeX/Method outline" 
FiguresFolder <- file.path(LatexFolder, "Figures")
TablesFolder <- file.path(LatexFolder, "Tables")
MatricesFolder <- file.path(LatexFolder, "Matrices")
Functions <-"/home/jonno/Create_ETYS_network/Functions"
Tariff <- file.path(basewd,"Tariff and Transport")
PLwd <- "/media/jonno/Seagate Expansion Drive/ProportionalLoading"

source("/home/jonno/Create_ETYS_network/SubCode/LoadData2.R")

```

#Create the Attack Orders
```{r}
#Set the path to a large enough storage
setwd(PLwd)

#Ensure there is powerflow
g <- PowerFlow(gbase, "FECK40")

AttackRounds <- 1000

#Create a reproducible attack order
seed<- 1589
filename <- "DeleteOrders100.rds"
if(file.exists(filename)){
  DeleteOrders <- readRDS(filename)
} else {
set.seed(seed)
DeleteOrders <- MultiAttackOrder(gbase, 100)  
saveRDS(DeleteOrders, filename)
}
```


#Perform Random attack on real line limits

```{r}
folder <- "Real_Limits"

  if(!file.exists(folder)){
    dir.create(folder)
  }

SaveMultiAttacks(g, DeleteOrders, folder, TotalAttackRounds = AttackRounds, CascadeMode = T)

```


#Generate PL networks

This function saves networks.
Should the function should be changed so that it can handle edges as well as nodes.

```{r}

#The vector of alpha values to be tested
#alpha_vector <- c(1.05, 1.1, 1.2, 1.5, 2, 3, 5)
alpha_vector <- c( 5)

#Create the simulations for each of the alpha avalues using 100 simulations for each
alpha_vector %>% walk(~{
  gProp <- Proportional_Load(g, alpha = .x)
  
  folder <- paste0("alpha_value_",  .x*100)
  #create folder if it doesn't already exist
  if(!file.exists(folder)){
    dir.create(folder)
  }
  
  SaveMultiAttacks(gProp, DeleteOrders, folder, TotalAttackRounds = AttackRounds, CascadeMode = T)
  
}
  
)
  
```

##Extend the experiment
This is used to extend the original experiment from 150 node removals to complete collapse
```{r}

# setwd(PLwd)
# directories <- list.dirs()
# 
# directories[grepl("value_",directories)][-c(1,2,3,4,5,6)] %>% 
#   walk(~{
#     setwd(file.path(PLwd, .x))
#     print(.x)
#     ExtendMulltiAttack(list.files(), DeleteOrders)
#     gc()
#   }
# )


```



#Extracting stats

Extracting stats is slow this extracts the stats and saves them as a file.

```{r}
Propfolder <- "/media/jonno/Seagate Expansion Drive/ProportionalLoading"


Sim_summary <- list.files(Propfolder, patter = "(alpha)|(Random)") %>% 
  file.path(Propfolder,.) %>% map_df(~{
    
    rootfolder <- .x
    targetfolder <- basename(.x)
    
    if(!file.exists(paste0(targetfolder, ".rds"))){
      
      print(paste("Extracting summary data for", targetfolder))
      
      summarydata <-list.files( rootfolder) %>% 
          map_df(~read_rds(file.path(rootfolder, .x)) %>%
                   ExtractNetworkStats()) %>%
          mutate(Cascade = TRUE, 
                 alpha = targetfolder,
                 simulationID = .x)
      savename <-paste0(targetfolder, ".rds")
      
      saveRDS(summarydata, savename)  
      
      print(paste("File", savename, "saved"))
      
    } else {print(paste("saved file for" , targetfolder, "exists"))}
  
    }
  )

#temp fix needs to be done properly
AttackRoundData <- list.files(pattern = ".rds")[-8] %>%
  map_df(~read_rds(.x))


```


#Construct attack summaries

Plots simple graphs from summary data

```{r}
SummariseMonteCarlo <- function(df){
 df %>% 
    mutate(PGfract = (max(PowerGen)- PowerGen)/max(PowerGen)) %>%
    group_by(NodesAttacked, alpha) %>%
    summarise(mean = mean(GCfract),
              sd = sd(GCfract),
              GC95 = quantile(GCfract, .95),
              GC05 = quantile(GCfract, .05),
              count = n(),
              mPGfract = mean(PGfract),
              sdPGfract = sd(PGfract),
              medPGfract = median(PGfract),
              PG95 = quantile(PGfract, .95),
              PG05 = quantile(PGfract, .05),
              PGmax = max(PGfract),
              PGmin = min(PGfract),
              mLoad = mean(GridLoading, na.rm = T),
              GL95 = quantile(GridLoading, .95, na.rm = T),
              GL05 = quantile(GridLoading, .05, na.rm = T)) %>%
    ungroup %>%
    group_by(alpha) %>%
     mutate(ID =n():1) %>%
    ungroup
  
}


SummaryofGC<- AttackRoundData %>%
  SummariseMonteCarlo %>%
  mutate(PercNum = NodesAttacked/958)

PNodeDens <-  AttackRoundData %>%
  mutate(PercNum = round(NodesAttacked*100/958),
            LoadDrop = (first(GridLoading)-GridLoading)/first(GridLoading))


SummaryofGC %>%
    ggplot(aes(x= PercNum, y = mean, colour = alpha)) +geom_line() +
    geom_ribbon(aes(ymin=GL05, ymax=GL95, fill = Cascade), alpha = 0.3)


test2 <- PNodeDens  %>%
  select(GCfract, Blackout, alpha, PercNum) %>%
  gather(., key="Type", value = "value",GCfract, Blackout) %>%
  mutate(Type = ifelse(Type == "GCfract","Giant componant size reduction", "Blackout size"))
  

 test2   %>%
  mutate(  PercAttacked= fct_rev(as_factor(paste0(PercNum, "%"))))  %>%
  ggplot(aes(y = PercAttacked)) +
  geom_density_ridges(aes(x = value, fill = alpha), alpha = 0.5)  + 
  scale_x_continuous(labels=scales::percent)  +
      facet_grid(~Type) +
  labs(x = "Performance drop", y = "Percent of elements attacked",
       title = "Change in the performance distribution as number of attacks increase") 


 NodeCollapse <- rbind(SummaryofGC %>%
  select(PercNum, mean, alpha, GC05, GC95, sd) %>% mutate(type = "Giant componant size reduction"),
SummaryofGC %>% 
  select(PercNum, mPGfract, alpha, PG05, PG95, sdPGfract) %>% mutate(type = "Blackout size") %>%
  rename(mean = mPGfract, GC05 = PG05, GC95 = PG95, sd = sdPGfract)
) %>% mutate(Target = "Node")

 
 NodeCollapse %>%
    ggplot(aes(x= PercNum, y = mean, colour = alpha)) +geom_line() +
   # geom_ribbon(aes(ymin=GC05, ymax=GC95, fill = alpha), alpha = 0.3) + 
  scale_x_continuous(labels=scales::percent) + 
  scale_y_continuous(labels=scales::percent) +
  facet_grid(~type) +
  labs(title = "Change in Giant Componant and Blackout size as nodes are attacked" , x = "Percent of elements attacked", y = "Performance drop")
 
 
  NodeCollapse %>%
    ggplot(aes(x= PercNum, y =sd, colour = alpha)) +geom_line() +
   # geom_ribbon(aes(ymin=GC05, ymax=GC95, fill = alpha), alpha = 0.3) + 
  scale_x_continuous(labels=scales::percent) + 
  scale_y_continuous(labels=scales::percent) +
  facet_grid(~type) +
  labs(title = "Size of 95-05 confidence interval as attack developes" , x = "Percent of elements attacked", y = "standard deviation")
 
```


#Deletion similarity

Get the round number that an edge was deleted.


```{r}
    
Removeddf <- list.files() %>% map_df(~{
 file <- .x
  print(file)
  read_rds(file ) %>%
  RoundRemoved()  %>%
    mutate(Sim = gsub(".rds", "",file))
  
  
  }
) %>%
  group_by(Sim) %>%
  mutate(RoundRemoved = ifelse(is.na(RoundRemoved), max(RoundRemoved), RoundRemoved))

Removeddf2 <- Removeddf %>%
  spread(., key = Sim, value = RoundRemoved)



setwd("/home/jonno/BigHeat")

list.files(pattern = ".r") %>%
  walk(~{source(.x)})


test2 <- Removeddf2 %>%
  select(-Edges) %>% t %>% cor()

test3 <- orderedheat(test2, simMat = T, mid =0.0)
test3

NL <- read_rds("Simulation_ID_1.rds" ) %>%
  RoundRemoved()
  
NLmat1 <- rep(NL$RoundRemoved, each = length(NL$RoundRemoved)) 

NLmat2 <- rep(NL$RoundRemoved, times = length(NL$RoundRemoved))

NLmat3 <- matrix(as.integer(NLmat1 == NLmat2), nrow=nrow(NL))


gtest <-graph_from_adjacency_matrix(NLmat3) %>%
  simplify() %>% delete.vertices(., degree(.)==0)


plot(gtest)

```


#Analyse results


#Tweaking the package
The below code is used to tweak the R package, add to the documentation etc, etc

```{r}
library(devtools)
library(roxygen2)
setwd( "/home/jonno/PowerGridNetworking")
document()
setwd("/home/jonno")
install("PowerGridNetworking")
library(PowerGridNetworking)

```


```{r}
setwd("/home/jonno")

install("PowerGridNetworking")

```

